---
title: "CRB Scenario Discovery"
author: "Nathan Bonham"
date: "July 8, 2021"
output: 
  flexdashboard::flex_dashboard:
    source_code: "https://github.com/nabocrb/CRB-Scenario-Discovery-App"
    theme: spacelab
    
    
runtime: shiny

---

```{r setup, include=FALSE}

# my sdprim wrapper function
source("SD function library.R")

### data loaded in SD function library.R

```



```{r, settings bsModal}

bsModal(id = "settingsModal", title = "Settings", trigger = "openModal", size = "large",
        
        
        h3("Scatter matrix options"),
        
        fluidRow(column(width=4, 
                  sliderInput(inputId = "legendx",label = "legend x position", min = 0.2, max = 0.75,value = 0.4, step = 0.01, width="200px", ticks = F)),
                 column(width=4, offset = 0,
                  sliderInput(inputId = "legendy",label = "legend y position", min = 0.7, max = 1,value = 0.94, step = 0.01, width="200px", ticks = F)      
                   
                    )
                 ),

                fluidRow(column(width=4, 
                  sliderInput(inputId = "scatterLabel", label = "Label font size", min = 10, max = 30, value = 16, step = 0.5,width = "200px", ticks = F)
                  ),
                 column(width=4, offset =0,
                  sliderInput(inputId = "scatterTick", label = "Tick font size", min = 8, max = 26, value = 12, step = 0.5,width = "200px", ticks = F)   
                    )
                 ),
        
        prettyToggle(inputId = "DiagonalTF",label_on = "Remove kernel density plots", label_off = "Include kernel density plots", value = T),
        
        
        splitLayout(cellWidths = c(320,20),h3("Violin plot download options"), circleButton(inputId = "imageHelp", icon=icon("info-circle"), size = "xs")),

bsTooltip(id="imageHelp", title = "Set height, width, and other parameters when downloading the violin plots (Part 2) as an image. The default height and width produce a .jpeg or .png with 960 dpi that scales nicely on 8.5 x 11 inch paper. The -Label and title scale- may need increased if larger images are downloaded. If .pdf is desired, you can download as .svg then use free online applications to convert from .svg to .pdf. Use these options in conjunction with the label options above to produce quality images.", placement = "right", options=list(container="body")),

splitLayout(cellWidths = c(300,300), 
            sliderInput(inputId = "height",label = "Image height (px)",min = 100, max=1000, value = 500, width=250, step = 50),
            sliderInput(inputId = "width",label = "Image width (px)",min = 250, max=2000, value = 500, width=250, step=50)
            
            ),


splitLayout(cellWidths = c(300,300), 
            
            sliderInput(inputId = "scale",label = "Label and title scale",min =1, max=17, value = 10, width=250),
            radioButtons(inputId = "format", label = "Image format", choices = c("jpeg", "png", "svg", "webp"), selected = "jpeg", width=250, inline=TRUE)
            
            )
        
          
        )


### toggle modal, for multiple action buttons

modalTrigger=reactiveValues(Obj=0, PT=0)

observeEvent(input$openModalObj, {
  
  toggleModal(session = session, modalId = "settingsModal", toggle = "open")
  
}, ignoreInit = T)







```


```{r, rolling window length Modal}

output$RollingAVGimage=renderImage({

          filename <- normalizePath("images/Rolling AVG.png")


          list(src=filename, width="640px", height="570px")

        }, deleteFile = F)

bsModal(id="WindowHelpModal", title = "Measuring streamflow with retrospective observation windows", trigger = "WindowHelp1",
        
                renderText("The table below shows an example calculation of the maximum and minimum 5-yr average flow. First, the five year rolling average of the PREVIOUS five years is calculated. For example, the five year rolling average at the end of 2021 is the average of years 2017 to 2021. Then, the maximum and minimum of the 5-yr averages are taken as the observable conditions. We chose to use the previous years of flow, rather the upcoming years, such that the metrics are directly observable and can be implemented in a signpost and adaptation monitoring system. For example, imagine that Scenario Discovery indicates a policy fails performance thresholds when the minimum five year average flow is below 11 MAF. If the policy were implemented in real life and you observe that the average flow over the previous five years is less than 11 MAF, then adaptive action may be needed. Use the dropdown menu to select the window length. If you select -44-, then the uncertainty metric is simply the mean flow over the simulation. If you select -any-, then the Scenario Discovery algorithm will be run with all window lengths. This is not recommended as it is computationally expensive, difficult to plot, and the results may use redundant or difficult-to-interpret metric combinations."),
        
        div(style="margin-bottom: 20px"),
        
        imageOutput("RollingAVGimage"),
        
        div(style="margin-bottom: 150px")
        

        
        )


```

```{r, Q thresholds modal, out.width = "50%", out.height = "50%"}

        output$Qthreshimage=renderImage({

          filename <- normalizePath("images/QThresh.png")


          list(src=filename)

        }, deleteFile = F)


output$FreqDurCalcimage=renderImage({

          filename <- normalizePath("images/Duration Frequency example.png")


          list(src=filename, width="550px", height="570px")

        }, deleteFile = F)

# filename=normalizePath("images/Vulnerability threshold.png")


bsModal(id="QThreshHelpModal", title = "Duration and frequency of high flows and low flows", trigger = "QThreshHelp1",
#         


        renderText("Duration and frequency time-series statistics are used to complement the rolling window statistics, providing a nuanced understanding of how some magnitude of flow can be realized by different frequency and durations of high flow and low flow years. However, quantifying duration and frequency requires us to select thresholds to define high flow and low flow. We define three alternate definitions of low flow and high flow, as shown in the figure below, each of which is based on the observed historical record at Lees Ferry. First, thresholds are defined using averages over renowned historical periods: a low flow is below the average of the drought of recent years (2000-2018), and a high flow is greater than the average of the wet period during which the Colorado River Compact was signed, termed the pluvial period (1906-1931). Second, thresholds are defined with terciles, which Reclamation has used in the past to describe high and low flows. Lastly, the thresholds are defined as the average plus or minus one standard deviation. Use the dropdown menu to select which threshold type to use with Scenario Discovery. Ultimately, Scenario Discovery will indicate which threshold type is most skilled for predicting vulnerability; however, it is important to choose a threshold definition that is understood and accepted by CRB stakeholders."),

        imageOutput("Qthreshimage"),
        
        div(style="margin-bottom:900px"),

        renderText("The above figure shows the three threshold types. The vertical axis shows annual stream flow in million-acre feet (maf) from 1906 to 2018, and the horizontal axis is the empirical return period in years."),

        div(style="margin-bottom:20px"),

        renderText("The table below shows an example calculation of duration and frequency for non-high flow years using historical thresholds. First, each year in the flow time-series is labelled as TRUE (high flow) or FALSE  (non-high flow) in the -High flow- column. Next, the -Count non-high- column records the number of consecutive non-high flow years. The maximum duration is the maximum value in this column, highlighted in orange. The average is the average number of years non-high flows persist, or the average of 7 and 3 (shown in green border). Frequency is the count of non-high flow years, or the number of FALSE values (highlighted in blue)."),

div(style="margin-bottom:20px"),

        imageOutput("FreqDurCalcimage"),

div(style="margin-bottom:300px")

        # knitr::include_graphics(filename)



)

```

```{r, observable conditions modal}

output$UMtable=renderImage({

          filename <- normalizePath("images/Uncertainty metrics table.png")


          list(src=filename, width="570px", height="520px")

        }, deleteFile = F)

bsModal(id = "MetricsHelpModal", title = "Observable conditions", trigger = "MetricsHelp1",
        
        renderText("Observable conditions (AKA uncertainty metrics) quantify important variables in the Colorado River Basin that we do not control, yet they affect the performance of the system. These metrics are uncertain because we do not know the magnitude of them in the future. The table below summarizes the observable conditions used in this study. Broadly speaking, we consider three sources of uncertainty: annual streamflow at Lees Ferry, AZ, initial system conditions, and water demand. To characterize hydrologic uncertainty, we calculate average annual flow in moving windows from 2 to 20 years in length. Moreover, we calculate duration and frequency metrics to provide a nuanced understanding of how different flow patterns may produce similar average flows. For additional information on the hydrology metrics, please use their information buttons found in the dropdown menu. For initial system conditions, we consider the pool elevations of Lake Mead and Lake Powell. The final metric is demand, which is the volume of water consumed by the Upper Basin states annually. Use this drop down menu to select which annual flow metrics to use in the Scenario Discover algorithm. Note that system condition and demand metrics are always passed to Scenario Discovery."),
        
        div(style="margin-bottom:20px"),
        
        imageOutput("UMtable"),
        
        div(style="margin-bottom:220px")
        
        )

```

```{r, density vs coverage Modal}

output$CoverageDensity=renderImage({
  
            filename <- normalizePath("images/DensityCoverage.png")


          list(src=filename, width="570px", height="300px")
  
}, deleteFile = F)

bsModal(id="PTModal", title = "Peeling trajectory, density, and coverage",trigger = "openPTModal", 
          
        renderText("The peeling trajectory plot is a scatter plot of density versus coverage, where each point is one scenario box found with the Scenario Discovery algorithm. Density and coverage are two metrics of scenario quality, the definitions of which are depicted in the figure below. Each plot shows States of The World plotted in two-dimensional space, where those two dimensions are observable conditions. The SOW are colored according to if they are vulnerable (failed performance thresholds) or not vulnerable (met performance thresholds). The red boxes represent scenarios, describing the upper and lower limits of observable conditions that describe the characteristics of SOW where performance thresholds are transgressed. The scenario box in the left plot has perfect density and coverage, capturing only and all of the vulnerable cases. In this ideal case, both density and coverage equal 1. The middle plot shows perfect coverage because all vulnerable cases are contained in the box, but imperfect density because there exists non-vulnerable cases in the box. The plot on the right shows the opposite case of perfect density, but coverage less than one. Keep in mind that SOW have more than two observable conditions, and thus the scenario boxes can also exceed two-dimensions, although scenarios with fewer dimensions are generally more interpretable."),
        
        div(style="margin-bottom: 10px"),
        
        renderText("It is your job to choose a scenario box by clicking on a point in the peeling trajectory. The scenarios will exhibit tradeoffs between density, coverage, and the number of observable conditions used, so use the peeling trajectory along with the scenario box plots to the right to explore."),
        
        div(style="margin-bottom: 30px"),
        
          imageOutput("CoverageDensity")
          
          )

```


```{r, manual thresholds modal}

bsModal(id = "ThresholdsModal", title = "Set thresholds with the sliders below", trigger = "openManualThresh",

    renderUI({
    req(length(input$SDObj) >=1)
    sliderInput("Thresh1", label=paste0(input$SDObj[1], " threshold"), min=min(obj_all[[input$SDObj[1]]]),
                max=max(obj_all[[input$SDObj[1]]]), value=max(obj_all[[input$SDObj[1]]]))
    }),
    
    renderUI({
    req(length(input$SDObj) >=2)
    sliderInput("Thresh2", label=paste0(input$SDObj[2], " threshold"), min=min(obj_all[[input$SDObj[2]]]),
                max=max(obj_all[[input$SDObj[2]]]), value=max(obj_all[[input$SDObj[2]]]))
    }),
    
    renderUI({
    req(length(input$SDObj) >=3)
    sliderInput("Thresh3", label=paste0(input$SDObj[3], " threshold"), min=min(obj_all[[input$SDObj[3]]]),
                max=max(obj_all[[input$SDObj[3]]]), value=max(obj_all[[input$SDObj[3]]]))
    }),
    
    renderUI({
    req(length(input$SDObj) >=4)
    sliderInput("Thresh4", label=paste0(input$SDObj[4], " threshold"), min=min(obj_all[[input$SDObj[4]]]),
                max=max(obj_all[[input$SDObj[4]]]), value=max(obj_all[[input$SDObj[4]]]))
    }),
    
    renderUI({
    req(length(input$SDObj) >=5)
    sliderInput("Thresh5", label=paste0(input$SDObj[5], " threshold"), min=min(obj_all[[input$SDObj[5]]]),
                max=max(obj_all[[input$SDObj[5]]]), value=max(obj_all[[input$SDObj[5]]]))
    }),

    renderUI({
    req(length(input$SDObj) >=6)
    sliderInput("Thresh6", label=paste0(input$SDObj[6], " threshold"), min=min(obj_all[[input$SDObj[6]]]),
                max=max(obj_all[[input$SDObj[6]]]), value=max(obj_all[[input$SDObj[6]]]))
    }),

    renderUI({
    req(length(input$SDObj) >=7)
    sliderInput("Thresh7", label=paste0(input$SDObj[7], " threshold"), min=min(obj_all[[input$SDObj[7]]]),
                max=max(obj_all[[input$SDObj[7]]]), value=max(obj_all[[input$SDObj[7]]]))
    }),

    renderUI({
    req(length(input$SDObj) >=8)
    sliderInput("Thresh8", label=paste0(input$SDObj[8], " threshold"), min=min(obj_all[[input$SDObj[8]]]),
                max=max(obj_all[[input$SDObj[8]]]), value=max(obj_all[[input$SDObj[8]]]))
    }),

    renderUI({
    req(length(input$SDObj) >=9)
    sliderInput("Thresh9", label=paste0(input$SDObj[9], " threshold"), min=min(obj_all[[input$SDObj[9]]]),
                max=max(obj_all[[input$SDObj[9]]]), value=max(obj_all[[input$SDObj[9]]]))
    }),
    
    renderUI({
      req(length(input$SDObj) >=1)
      actionButton(inputId = "COImanual", label = "Apply thresholds & plot", width = "35%")
      
    })



        )


```




Introduction 
=================================================

### 

```{r, intro figure}

output$IntroFig=renderImage({

          filename <- normalizePath("images/Overview.png")


          list(src=filename, width="1485px", height="860px")

        }, deleteFile = F)

fluidRow(column(width=11, offset = 1,
        imageOutput("IntroFig")        
                ))

absolutePanel(
  
  actionButton(inputId = "RobustnessApp",label = "Open robustness app", onclick="location.href='https://nabocrb.shinyapps.io/CRB-Robustness-App-Shiny-Contest';", width = "110%"),
  
  class = "panel panel-default", fixed = T,
                draggable = TRUE, top = "auto", bottom=20, left = 10, right = "auto",
                width = '8%', height = 'auto',
                style = "style = z-index: 400"
  
)

```



1. Define vulnerability thresholds { data-orientation=columns}
==================================================

Column {data-width=300}
-----------------------

### Part 1: Select policy, observable conditions, and objectives to plot {data-height=200}

```{r}

# data-navmenu="Scenario Discovery-1"

sidebarPanel(width=5, style={"margin-left: -20px; margin-right: -15px"},
  
selectInput(inputId = "policyID",label = "Select policy ID", choices = 1:nrow(wide_data)),

selectInput(inputId = "policyIDcompare",label = "Select policy(s) to compare", choices = c(1:nrow(wide_data)), selected = NULL, multiple = T),


fluidRow(column(width=9, #fluidRow for dropdown button

           dropdownButton(circle = F, label = "Observable conditions",width = "160%",inputId = "UMdropdown", 
                        
prettyToggle(inputId = "manualMetricSelectionTF",label_on = "Select conditions by window length",label_off = "Select conditions with drop down list", value = T),

renderUI({
  
  req(input$manualMetricSelectionTF==FALSE)
  
  selectInput(inputId = "manualSelection", label = "Choose observable conditions for Scenario Discovery", choices =colnames(SOW_all[-c(4,5)]),multiple = T)
  
}),
                        
fluidRow(column(width=10,
                
renderUI({
    req(input$manualMetricSelectionTF==T)
            selectInput(inputId = "Window", label = "Select moving window length (years)",choices = c("2", "5", "8", "10", "20", "44", "any"), selected = "10")
                })),

         column(width = 1, offset = 0,
          
                renderUI({
                    req(input$manualMetricSelectionTF==T)
                
            circleButton(inputId = "WindowHelp1", icon = icon("info-circle"), size = "xs")
            
                })
            
                )
         )

,

  fluidRow(column(width=10,

          renderUI({
                    req(input$manualMetricSelectionTF==T)        
                  
           prettyToggle(inputId = "DurFreq",label_on = "Include duration metrics",label_off = "Exclude duration metrics", value = TRUE)

                })),
         column(width = 1, offset = 0,
                
            renderUI({
                    req(input$manualMetricSelectionTF==T)
                    
            circleButton(inputId = "QThreshHelp1", icon = icon("info-circle"), size = "xs")
            
            })
            
                )
         ),



renderUI({
  
  req(input$manualMetricSelectionTF==T)
  req(input$DurFreq==TRUE)
              selectInput(inputId = "QThreshType",label = "High vs low flow year definition type", choices = c("historical", "terciles", "mean & standard deviation"), selected = "historical")

}),

    renderUI({
      selectInput("PlotMetrics",label="Select observable conditions to plot", multiple = T, choices=colnames(x$x))
      })

               ) # end drop down button



), # end column for dropdownButton

         column(width = 1, offset = 0,
            circleButton(inputId = "MetricsHelp1", icon = icon("info-circle"), size = "xs", style="margin-left:20px")
                )), # end fluidRow for dropdownButton and info button

div(style="margin-bottom:10px"), # adds padding between buttons

selectInput(inputId = "SOWensemble", label = "Choose SOW ensemble", choices = c("cLHS 300", "cLHS 500"), selected = "cLHS 300"),

selectInput("SDObj",label="Select objectives for scenario discovery", multiple = T, choices=colnames(obj_all)[-c(1,2)]),

radioButtons(inputId = "AndOr", label = "Condition for multiple objectives", choices = c("Or", "And"), inline = T)

         ) # end sidebarPanel

bsTooltip(id = "AndOr",title = "In the case you have set thresholds on multiple objectives, define whether vulnerability is defined by the union (Or) or intersection (And) of the thresholds. For -Or-, an SOW is classified as vulnerable if either of the thresholds are violated (expect more vulnerable cases). For -And-, an SOW is classified as vulnerable if both thresholds are violated (expect less vulnerable cases).", placement = "right", options=list(container="body"))


output$DVplot=renderPlotly({
  
        if (isTruthy(input$policyIDcompare)){
          IDs=c(input$policyID, input$policyIDcompare)
        } else {
          IDs=input$policyID
        }
  
  
        DV_plot(to_plot=IDs, metric_label="order", preferred_direction="min", y_axis2=F)
  
      })

mainPanel(width = 7,
          plotlyOutput("DVplot", height="auto")
          )

####################### tooltips ###########################

# bsTooltip(id = "UMdropdown", title = "Select observable conditions for use in the Scenario Discovery algorithm and for plotting in the scatter matrix to the right. See the tooltips and information buttons for each user entry for more.", placement = "right", options=list(container="body") )

bsTooltip(id="DurFreq", title = "These metrics measure both the duration and frequency of high flow years, low flow years, and non-high flow years. One of three different types of thresholds can be selected to define high flow vs low flow. Please use the information button to the right for descriptions of the thresholds and metrics.",  placement = "right", options=list(container="body") )

bsTooltip(id="PlotMetrics", title = "Choose metrics to plot in the scatter matrix to the right. Please note that the metrics chosen here only affect the plot, but all metrics with the chosen window length high/low flow definition type are inputs to the Scenario Discovery algorithm.",  placement = "right", options=list(container="body"))

bsTooltip(id="policyID", title = "Choose the policy ID you desire to perform Scenario Discovery on.", placement = "right", options=list(container="body") )

bsTooltip(id = "policyIDcompare", title = "You may select additional policies to compare to the policy selected above. They are plotted both in the decision variable plot to the right and the violin plots below.",  placement = "right", options=list(container="body"))

bsTooltip(id = "SDObj", title = "Select optimization objectives. In Part 2 below, you can select performance thresholds that define acceptable [not vulnerable] from unacceptable [vulnerable] performance Moreover, these objectives are plotted in the scatter plot matrix to the right.",  placement = "right", options=list(container="body"))

```


### 
```{r, violin plots}

fluidRow(column(width = 10, offset = 0,
              h5("Part 2: Select performance thresholds by moving the dashed black lines", style="margin-top: 3px; 
                 margin-bottom: 8px")  
              ),
         column(width=1, offset=1,
    circleButton(inputId = "openManualThresh", icon = icon("sliders-h"), size = "xs")
                )
         
         )
bsTooltip(id = "openManualThresh", title = "Instead of interacting with the violin plots directly, define thresholds manually by clicking this button. Please make sure to select objectives first.", options=list(container="body"), placement = "right")

hr(style="margin-botom: 0px; margin-top: 0px; margin-left: -10px", width="110%")

update=reactiveValues(thresholds=0, PRIMalg=0, ensemble=0, policy=0, policy2=0, thresholds2=0, ensemble2=0, AndOr=0, AndOr2=0, currentEnsemble="cLHS 500", currentAlg=F, currentPolicy=1, currentAndOr="Or") # used to place asterisks on plots and tables that need updated, and the corresponding buttons to perform the update

observeEvent(input$policyID !=update$currentPolicy, { # want to ignore initiliaztion for the update trigger
  
  # cat(file=stderr(), 'ensembles:', c(input$SOWensemble, update$currentEnsemble), "\n")
  
  req(input$policyID !=update$currentPolicy)
  
  update$policy=1
  update$policy2=1
  
  update$currentPolicy=input$policyID

}, ignoreInit = T)

observeEvent(input$AndOr !=update$currentAndOr, { # want to ignore initiliaztion for the update trigger


  req(input$AndOr !=update$currentAndOr)
  
  update$AndOr=1
  update$AndOr2=1
  
  update$currentAndOr=input$AndOr

}, ignoreInit = T)


observeEvent(list(update$thresholds, update$ensemble, update$policy, update$AndOr),{
  
  #cat(file=stderr(), 'your name:', c(update$thresholds, update$ensemble), "\n")
  
  update$COIbutton=ifelse(
    sum(update$thresholds, update$ensemble, update$policy, update$AndOr)>0,
    "*Apply thresholds & plot*",
    "Apply thresholds & plot"
  )
  
})

fluidRow(

  column(width=3,
  renderUI({
  
  actionButton('COIButton',label=update$COIbutton, width="140%", style="margin-right: 0px; margin-top:-5px")  
  })      
    ),

  column(width=3, offset=1,

         div(style="margin-top: -5px",
          
         dropdownButton(circle = F,label = "Round threshold to nearest:", width = "150%", margin = "10px",

                        radioButtons(inputId = "RoundTo", label = NULL, choices = c("no rounding","0.01", "0.1", "1", "10", "100"),selected = "no rounding")

                        )
         
                )

         ),


  column(width=3, offset=1,
  actionButton("ResetThresholds", label="Reset all thresholds", width="120%", style="margin-left: 25px; margin-top:-5px")
  )
  )


names=colnames(obj_all)[-c(1,2)]
  my_units=c("KAF", "KAF", "%", "%", "%", "Yrs", "%", "KAF", "MAF")
units.df=data.frame(matrix(nrow=1, ncol=length(my_units)))
colnames(units.df)=names
units.df[1,]=my_units


output$VP= renderPlotly({

  validate(need(input$SDObj, "Select objectives to plot"))

  input$ResetThresholds # reset lines if Reset all thresholds button is hit
  input$COImanual #reset lines if manual thresholds are entered
  
  
  data=dplyr::filter(x$obj, ID %in% input$policyID)

  units=as.vector(units.df[,input$SDObj])

  y_vec=vector(length = length(input$SDObj))

  
  thresh_temp=isolate(thresholds$thresholds)  # need to isolate so violin plots are not redrawn every time the threshold line is moved
  obj_temp=isolate(thresholds$objectives)


for(i in 1:length(input$SDObj)){

  if(input$SDObj[i] %in% obj_temp){
    y_vec[i]=thresh_temp[which(obj_temp==input$SDObj[i])]
  } else {
    y_vec[i]=max(data[,input$SDObj[i]])
  }

}
  add_to_title=""
  if(isTruthy(input$policyIDcompare)){

    policyIDs=input$policyIDcompare

    TF=T

    for(i in 1:length(input$policyIDcompare)){
      if(i==1){
        add_to_title=paste0(", ",input$policyIDcompare[i])

      } else {

        add_to_title=paste0(add_to_title, add_to_title=paste0(", ",input$policyIDcompare[i]))

      }


    }



  } else {
    policyIDs=NULL
    TF=F
  }

  a=violin_subplots(obj = data, source = "VP", obj_names = input$SDObj, unit_vec =units, y_vec =  y_vec, policyID=policyIDs,
      color_vec = c("blue", "gray", "pink", "red", "brown", "red"),  objectives_all=x$obj, add_traces=TF, firstpolicy=input$policyID, img_height=input$height, img_width=input$width, img_scale=input$scale,
                         img_format=input$format)

  a= a %>%layout(title=list(text=paste0("policy ID: ", input$policyID, add_to_title), y=0.98), margin=list(b=80,t=35,pad=0))
  a
  
  
})

plotlyOutput("VP")

```

```{r, add thresholds to violin plots}

thresholds=reactiveValues(objectives=NA, thresholds=NA, ManualThresholdsTrigger=0)

observeEvent(eventExpr = event_data("plotly_relayout", source = "VP"),{
  
  temp=event_data("plotly_relayout", source = "VP")
  
  ignore_check=names(temp)[1] #ignore all plotly relayout events that are NOT moving the line. When
  # the line is moved, the first element starts with shapes
  
  req(startsWith(ignore_check, "shapes[")) # ignore other types of relayout events
  
  tempIndex=regmatches(ignore_check, gregexpr("\\[.+?\\]", ignore_check))
  index=as.numeric(substr(x = tempIndex, start = 2, stop = 2))# extract the index from between the brackets
  input_names=isolate(input$SDObj)
  metric= input_names[index+1] # plus one for JS 0 index to R 1 index
  
  req(isTruthy(temp[[3]]))
  
  y=temp[[3]] # the third element corresponds to y0, ie the performance threshold
  
  ### round y to nearest [] based on user input
  
  RoundTo=isolate(input$RoundTo)
  
  if(RoundTo == "no rounding"){
    #nothing
  } else if(RoundTo=="0.01"){
    y=round(y, 2)
  } else if (RoundTo=="0.1"){
    y=round(y, 1)
  } else if (RoundTo=="1"){
    y=round(y)
  } else if (RoundTo=="10"){
    y=round(y, -1)
  } else if (RoundTo=="100"){
    y=round(y, -2)
  } else {
    #nothing
  }
  

  # add objective and threshold
  
  if(is.na(thresholds$thresholds[1])){
    thresholds$thresholds=y
    thresholds$objectives=metric
    
  } else if(metric %in% thresholds$objectives) {
    
    i=which(thresholds$objectives==metric)
    thresholds$thresholds[i]=y
    
  } else {
    
    thresholds$thresholds=c(thresholds$thresholds, y)
    thresholds$objectives=c(thresholds$objectives,metric)
  
  }
  
  
  update$thresholds=1
  update$thresholds2=1

}, ignoreInit = T, ignoreNULL = T)


observeEvent(input$SDObj, { # check if user has removed any objectives. If so, remove from threholds$objectivs and $thresholds
  
  #     cat(file=stderr(), 'length thresholds$objectives', length(thresholds$objectives), "\n") # prints dimension to R console
  # cat(file=stderr(), 'length input$SDObj', length(input$SDObj), "\n") # prints dimension to R console
  # 
  # 

  if(length(thresholds$objectives) > length(input$SDObj) ){ # user has removed objectives, need to remove from thresholds$objectives
    
    
    removeIndex=which(!(thresholds$objectives %in% input$SDObj))
    thresholds$objectives=thresholds$objectives[-removeIndex]
    thresholds$thresholds=thresholds$thresholds[-removeIndex]

  }
  
})

observeEvent(input$ResetThresholds, {
  
  # req(thresholds$objectives)
  
  data=dplyr::filter(obj_all, ID %in% input$policyID)

  thresholds$objectives=NULL
  thresholds$thresholds=NULL
  thresholds$objectives=NA
  thresholds$thresholds=NA
  
  y$COI=NULL
  y$nCOI=0
  y$nonCOI=length(y$COI)

  #update$thresholds=0
  
})



```


Column {.tabset .tabset-fade}
------------------------

### Observable conditions

```{r, observable conditions pairs plot}


renderPlot({

  data=x$x

  validate(need(y$COI, "Use the violin plots to define vulnerability thresholds."))
  validate(need(y$Trigger==1, "Use the violin plots to define vulnerability thresholds."))
  validate(need(input$PlotMetrics, "Select observable conditions."))
   validate(need(length(input$PlotMetrics)>1, "Select at least one more metric."))
     validate(need(length(y$COI)==nrow(obj$filter), "Apply thresholds after changing SOW ensemble."))

  # req(y$Trigger==1)
  yCOI=y$COI
  Vulnerable=ifelse(yCOI==1, "Yes", "No")

  data$Vulnerable=Vulnerable

  labelSize=input$scatterLabel
  tickSize=input$scatterTick
  
  diagInput=if(input$DiagonalTF==T){list(continuous = modified_density)} else {list(continuous = "blankDiag")}
  
  pairs_UM=ggpairs(data=data, columns = input$PlotMetrics,
        aes(color=Vulnerable, alpha=0.3),
        lower = list(continuous=modified_points),
        upper=list(continuous = "blank"), legend=NULL, switch="both", title="Vulnerable SOW",
        diag = diagInput)+
        theme(text=element_text(size=labelSize))

  pairs_UM=pairs_UM+theme(axis.text.x = element_text(angle=90, size=tickSize), axis.text.y = element_text(size=tickSize))

  temp_UM=pairs_UM[2,1] # extract plot to steal legend from

  temp_UM=temp_UM+theme(legend.key = element_rect(fill = "transparent", colour = "transparent"),
                rect = element_rect(fill = "white")) # make legend background transparent

  legend_UM=get_legend(temp_UM) #steal legend
  legend_UM=as_ggplot(legend_UM) # convert to ggplot

  x=input$legendx
  y=input$legendy
  
  if( input$DiagonalTF==F){
      pairs_UM=gpairs_lower(pairs_UM) # remove extra labels when diagonal not wanted
  }
  
  vp_UM=viewport(width = 1, height=2, x=x, y=y) # viewport for legend
  print(pairs_UM)
  print(legend_UM, vp=vp_UM)


})





```

```{r, absolute panel observable conditions}

# create the table displayed in the absolute panel

observe({
  
  c1=c(thresholds$objectives, "And/Or condition")
  c2=c(thresholds$thresholds, input$AndOr)
  
  thresholds$table=data.frame(objective=c1, threshold=c2)
  # thresholds$table=data.frame(objective=thresholds$objectives, threshold=thresholds$thresholds)
  

})

observeEvent(list(update$thresholds, update$ensemble, update$policy, y$nCOI), {
  
  update$SOWFraction=ifelse(sum(update$thresholds, update$ensemble, update$policy)>0,
                            paste0("*",y$nCOI, " / ", length(y$COI), "*"),
         paste0(y$nCOI, " / ", length(y$COI)))
})

absolutePanel(class = "panel panel-default", fixed = T,
                draggable = TRUE, top = 100, left = "auto", right = 20, bottom = "auto",
                width = '15%', height = 'auto',
                style = "overflow-y:scroll; max-height: 1000px; opacity: 0.9; style = z-index: 400",

              h4(strong("Vulnerability statistics")),
              
                 HTML('<button data-toggle="collapse"  data-target="#box2" class="btn-block btn-primary">Objective: threshold</button>'),
   tags$div(id = 'box2', class="collapse in",

      renderTable(thresholds$table)
      
      ),

      HTML('<button data-toggle="collapse" data-target="#box1" class="btn-block btn-primary">Number of vulnerable SOW</button>'),
      tags$div(id = 'box1', class="collapse in", align="center", style="margin-bottom: 10px",

               
        renderText(update$SOWFraction)),

   tags$div(id="buttonUM", align="center",
            
            div(style="margin-bottom:5px"),
            actionButton(inputId= "openModal",label = "Open plot settings", icon=icon("cog"), width = "160px"),
            div(style="margin-bottom:5px"),
            div(style="margin-bottom:5px")
            
            )

   )


```

### Objectives


```{r, objectives pairs plot}


renderPlot({
  
  data=obj$filter[-c(1,2)]

  validate(need(y$COI, "select vulnerability thresholds."))
  validate(need(y$Trigger==1, "select vulnerability thresholds."))
  validate(need(input$SDObj, "select at least two objectives."))
  validate(need(length(input$SDObj)>1, "select at least two objectives to plot."))
  validate(need(length(y$COI)==nrow(obj$filter), "Apply thresholds after changing SOW ensemble."))
  # req(y$Trigger==1)
  yCOI=y$COI
  Vulnerable=ifelse(yCOI==1, "Yes", "No")
  
  data$Vulnerable=Vulnerable
  
  labelSize=input$scatterLabel
  tickSize=input$scatterTick
  
  diagInput=if(input$DiagonalTF==T){list(continuous = modified_density)} else {list(continuous = "blankDiag")}
  
  pairs_obj=ggpairs(data=data, columns = input$SDObj,
        aes(color=Vulnerable, alpha=0.3),
        lower = list(continuous=modified_points),
        upper="blank", legend=NULL, switch="both", title="Vulnerable SOW",
        diag = diagInput)+
        theme(text=element_text(size=labelSize))
  
  pairs_obj=pairs_obj+theme(axis.text.x = element_text(angle=90, size=tickSize), axis.text.y = element_text(size=tickSize))
  
  temp_obj=pairs_obj[2,1] # extract plot to steal legend from

  temp_obj=temp_obj+theme(legend.key = element_rect(fill = "transparent", colour = "transparent"),
                rect = element_rect(fill = "white")) # make legend background transparent

  legend_obj=get_legend(temp_obj) #steal legend
  legend_obj=as_ggplot(legend_obj) # convert to ggplot

  x=input$legendx
  y=input$legendy
  
  if( input$DiagonalTF==F){
      pairs_obj=gpairs_lower(pairs_obj) # remove extra labels when diagonal not wanted
  }
  
  vp_obj=viewport(width = 1, height=2, x=x, y=y) # viewport for legend
  print(pairs_obj)
  print(legend_obj, vp=vp_obj)
  

})

  

```

```{r, absolute panel Objectives}

absolutePanel(class = "panel panel-default", fixed = T,
                draggable = TRUE, top = 100, left = "auto", right = 20, bottom = "auto",
                width = '15%', height = 'auto',
                style = "overflow-y:scroll; max-height: 1000px; opacity: 0.9; style = z-index: 400",

              h4(strong("Vulnerability statistics")),
              
         HTML('<button data-toggle="collapse" data-target="#boxObj2" class="btn-block btn-primary">Objective: threshold</button>'),
   tags$div(id = 'boxObj2', class="collapse in",

      renderTable(thresholds$table)
      
      ),
   

      HTML('<button data-toggle="collapse" data-target="#boxObj1" class="btn-block btn-primary">number of vulnerable SOW</button>'),
      tags$div(id = 'boxObj1', class="collapse in", align="center", style="margin-bottom: 10px",

        renderText(update$SOWFraction)),


   
   tags$div(id="buttonObj", align="center",
            
            div(style="margin-bottom:5px"),
            actionButton(inputId= "openModalObj",label = "Open plot settings", icon=icon("cog"), width = "160px"),
            div(style="margin-bottom:5px")
            )


   )


```


2. Perform Scenario Discovery { data-orientation=columns}
===========================================

```{r SD plot settings modal}

# data-navmenu="Scenario Discovery-1"

bsModal(id = "PlotSettingsSD", title = "Scenario Discovery settings",trigger = "OpenPlotSettingsSD",
        
        h3("Scenario Discovery algorithm"),
        
        hr(),

          fluidRow(column(width=5,
                  
              h5("Choose PRIM algorithm type:"),
prettyToggle(inputId = "PRIMType",label_on = "normal PRIM",label_off = "multi-objective PRIM", value = FALSE)            
                  ), column(width=5, 
                            
               radioButtons(inputId = "peel_crit", label = "Peeling objective function", choices = c(1, 2, 3), selected = 2, width=250, inline=TRUE)             
                            )),

        fluidRow(column(width=5,
                        
                 sliderInput(inputId = "QPval",label = "multi-objective PRIM p-value", min = 0.01, max = 0.5, value = 0.1, ticks = F, width="200px")       
                        ), column(width=5,
                                  
                sliderInput(inputId = "PeelAlpha",label = "PRIM peeling parameter", min = 0.01, max = 1, value = 0.05, ticks = F, width="200px")                  
                                  )),

        h3("Scenario boxes plot settings"),

        hr(),

        fluidRow(column(width = 5,
                  prettyToggle(inputId = "PlotSignificant", label_on = "Plot all metrics selected", label_off = "Plot only significant metrics", value = F) ),
                 column(width = 5,
                  prettyToggle(inputId = "SDDiagonalTF",label_on = "Remove kernel density plots", label_off = "Include kernel density plots", value = T)    )
                 ),

fluidRow(column(width=4, 
                  sliderInput(inputId = "SDlegendx",label = "legend x position", min = 0.05, max = 0.75,value = 0.4, step = 0.01, width="200px", ticks = F)),
                 column(width=4, offset = 0,
                  sliderInput(inputId = "SDlegendy",label = "legend y position", min = 0.05, max = 1,value = 0.94, step = 0.01, width="200px", ticks = F)      
                   
                    )
                 ),

                fluidRow(column(width=4, 
                  sliderInput(inputId = "SDscatterLabel", label = "Axis label font size", min = 10, max = 30, value = 16, step = 0.5,width = "200px", ticks = F)
                  ),
                 column(width=4, offset =0,
                  sliderInput(inputId = "SDscatterTick", label = "Tick font size", min = 8, max = 26, value = 12, step = 0.5,width = "200px", ticks = F)   
                    )

                 
                 ),


       sliderInput(inputId = "RangePlotFont",label = "Metric constraint font size", min = 2, max = 10, value = 5, step = 1 , width="30%", ticks = F)
                        

        
        )

observeEvent(input$PRIMType !=update$currentAlg, { # want to ignore initiliaztion for the update trigger
  
  # cat(file=stderr(), 'ensembles:', c(input$SOWensemble, update$currentEnsemble), "\n")
  
  req(input$PRIMType !=update$currentAlg)
  
  update$PRIMalg=1

  update$currentAlg=input$PRIMType

}, ignoreInit = T)


bsTooltip(id = "PRIMType", title = "Multi-objective PRIM differs from normal PRIM first by using only the metrics that pass a p-value statistical significance test. Further, it explicitly considers the objective to minimize the number of metrics used by testing all possible metric combinations for 1 to N number of significant metrics.", placement = "right", options=list(container="body"))

bsTooltip(id = "QPval", title = "Select the p-value threshold metrics must satisfy to be used with multi-objective PRIM. A higher p-value generally results in more metrics being used, but with more potential for over-fitting the data.", placement = "right", options=list(container="body"))

bsTooltip(id = "PeelAlpha", title = "The PRIM peeling parameter controls how patiently the algorithm peels away from the input space, where larger values are less patient and smaller values are more patient.",  placement = "right", options=list(container="body") )

bsTooltip(id = "peel_crit", title = "You can select from three objective functions for PRIM to create scenario boxes. Objective 1 is to maximize density inside the box. Objective 2 is to maximize density normalized by the support of the peeled box. Objective 3 is to minimize the number of non-vulnerable cases in the box being peeled away. For more information, see Friedman and Fisher 1999, equation 2.4 and section 14.1   ",  placement = "right", options=list(container="body") )

```

Column {data-width=225}
----------------------

```{r}
obj=reactiveValues(filter= dplyr::filter(obj_all, ID %in% 1))

observeEvent(list(input$policyID, input$SOWensemble) , {
  
  obj$filter=dplyr::filter(obj_all, ID %in% input$policyID)
  
  if(input$SOWensemble=="cLHS 300"){
    
    obj$filter=obj$filter[SOW_500_300_100[[2]]$model,]
  
  }
}, ignoreNULL = T, ignoreInit = T)


```

### {data-height=350}

```{r, user interface, include=TRUE}


observeEvent( list(update$thresholds2, update$PRIMalg, update$ensemble2, update$policy2, update$AndOr2) ,{

  update$SDButton=ifelse(sum(update$thresholds2, update$PRIMalg, update$ensemble2, update$policy2, update$AndOr2)>0,
         "*Perform scenario discovery",
                         "Perform scenario discovery")

})

sidebarPanel(width=5, style={"margin-left: -20px; margin-right: -20px; margin-top: 0px; margin-bottom: 0px"},
     
  # h4(strong("Scenario Discovery"), style="margin-top: -10px"), 
  
  # actionButton(inputId = "OpenModalSD", width="230px", label="Scenario Discovery settings", icon = icon("cog")),
  
  # circleButton(inputId = "OpenModalSD", icon = icon("cog"), size = "sm"),
  
  # div(style="margin-bottom:20px"),
  
  renderUI({
    actionButton(inputId = "SDButton",label = update$SDButton, width = "98%")
  }),
  
  div(style="margin-bottom:20px"),
  
  # h4(strong("Plot settings"),  style="margin-top: 10px"),
  
  
  actionButton(inputId = "OpenPlotSettingsSD", width="98%", label="PRIM and plot settings", icon = icon("cog")),
  
  div(style="margin-bottom:20px"),
  
  renderUI({
    req(box$ID)
    
    textInput(inputId = "ScenarioName", placeholder = "eg. Policy 7, 10yr, high density", label = "Enter scenario name to save", width = "230px" )
    
  }),
  
  renderUI({
    
    req(input$ScenarioName)
    req(box$ID)
    
    actionButton(inputId = "SaveScenario", label = "Save analysis", width = "98%", icon = icon("save"))
    
  })

                )

algorithm=reactiveValues()
observeEvent(input$PRIMType, {
  
  if(input$PRIMType==FALSE){
    algorithm$name="multi-objective PRIM"  
  } else {
    algorithm$name="normal PRIM"
  }
  
})

mainPanel(width=7,
          
  h5(strong("Vulnerability statistics")),

  HTML('<button data-toggle="collapse" data-target="#boxPTa" class="btn-block btn-primary">Policy ID</button>'),
      tags$div(id = 'boxPTa', class="collapse in", align="center",

        renderText(as.character(input$policyID))),
  
  
  
       HTML('<button data-toggle="collapse" data-target="#boxPT4" class="btn-block btn-primary">SOW ensemble</button>'),
   tags$div(id = 'boxPT4', class="collapse in", align="center",

      renderText(input$SOWensemble)),
  
     HTML('<button data-toggle="collapse" data-target="#boxPT2" class="btn-block btn-primary">Objective: threshold</button>'),
   tags$div(id = 'boxPT2', class="collapse in",

      renderTable(thresholds$table)),
  
  HTML('<button data-toggle="collapse" data-target="#boxPT" class="btn-block btn-primary">number of vulnerable SOW</button>'),
      tags$div(id = 'boxPT', class="collapse in", align="center",

        renderText(update$SOWFraction)),


  
     HTML('<button data-toggle="collapse" data-target="#boxPT3" class="btn-block btn-primary">Scenario Discovery algorithm</button>'),
   tags$div(id = 'boxPT3', class="collapse in", align="center",

      renderText(algorithm$name))
  
  
  )



```


```{r, choose SOW ensemble}

SOW_all=SOW_500_300_100[[1]]$SOW
SOW_all=dplyr::select(SOW_all, -matches(c("RolDef.", "median", ".Freq", "min")))
SOW_all=dplyr::select(SOW_all, -"max")



# initialize as cLHS 500
x=reactiveValues(ensemble=SOW_all, keep=colnames(SOW_all[, -c(4,5)]), x=SOW_all[, -c(4,5)], obj=obj_all, switchTrigger=0)

observeEvent(input$SOWensemble, {
  
  if (input$SOWensemble == "cLHS 300"){x$ensemble=SOW_500_300_100[[2]]$SOW} else {x$ensemble=SOW_500_300_100[[1]]$SOW}
  
  x$x=x$ensemble[, -c(4,5)]# remove Hydro Scenario and trace number
  
  x$x=dplyr::select(x$x, -matches(c("RolDef.", "median", ".Freq", "min")))
  x$x=dplyr::select(x$x, -"max")

  x$x=x$x[,x$keep] # subset by metrics user has selected
  
  
  ######### also update objectives
  
  if(input$SOWensemble == "cLHS 300"){
    x$obj=dplyr::filter(obj_all, TraceNumber %in% SOW_500_300_100[[2]]$model)
      # cat(file=stderr(), 'x$obj', length(unique(x$obj$TraceNumber)), "\n") # prints dimension to R console
  } else {
      x$obj=obj_all
      # cat(file=stderr(), 'x$obj', length(unique(x$obj$TraceNumber)), "\n")
    }
  
  
}, ignoreInit = F)

observeEvent(input$SOWensemble !=update$currentEnsemble, { # want to ignore initiliaztion for the update trigger
  
  # cat(file=stderr(), 'ensembles:', c(input$SOWensemble, update$currentEnsemble), "\n")
  
  req(input$SOWensemble !=update$currentEnsemble)
  
  update$ensemble=1
  update$ensemble2=1
  
  update$currentEnsemble=input$SOWensemble

}, ignoreInit = T)


```

```{r, filter observable conditions by UI}


### window length filter

observeEvent(input$Window,{ 
  
  yr=paste0(input$Window, "yr")
  
  always_keep=c("Demand", "Mead.PE", "Powell.PE")
  
  if(yr=="anyyr"){
    # do nothing
  } else if (yr=="44yr") {
    # mean, median
    
    # keep=colnames(SOW_all)[grep(pattern="Q", x = colnames(SOW_all))] # Frequency and duration of high vs low flow years
    
    cols=c(always_keep, "mean")
    
    x$window=cols
    
  } else {
    

    keep=colnames(SOW_all)[grep(pattern=yr, x = colnames(SOW_all))]
    cols=c(always_keep, keep)
    
    x$window=cols

    
    
  }
  
  
}, ignoreInit = F)

### high vs low flow threshold type filter filter

observeEvent(input$QThreshType,{ 
  
  # req(input$DurFreq==TRUE)
  type=input$QThreshType

  if (type=="historical"){
    
    keep=colnames(SOW_all)[grep(pattern=".hist", x = colnames(SOW_all))]
    
  } else if (type=="terciles") {

    keep=colnames(SOW_all)[grep(pattern=".ter", x = colnames(SOW_all))]

  } else { # mean & standard deviation
    
    keep=colnames(SOW_all)[grep(pattern=".SD", x = colnames(SOW_all))]

  }
  
  x$QThreshType=keep

}, ignoreInit = F)

# update metrics depending on if duration and frequency are included or excluded
observeEvent(list(x$QThreshType, x$window, input$DurFreq),{


  if (!isTruthy(x$QThreshType)){
    x$keep=x$window
  } else if (input$DurFreq==FALSE){
    x$keep=x$window
  } else {
    x$keep=c(x$window, x$QThreshType)
  }

  x$switchTrigger=0
  
})

observeEvent(x$switchTrigger==1,{


  if (!isTruthy(x$QThreshType)){
    x$keep=x$window
  } else if (input$DurFreq==FALSE){
    x$keep=x$window
  } else {
    x$keep=c(x$window, x$QThreshType)
  }

  x$switchTrigger=0
  
})

observeEvent(list(input$manualMetricSelectionTF, input$manualSelection),{
  
  x$keep=input$manualSelection
  # cat(file=stderr(), 'x$keep', x$keep, "\n")  

  req(isTruthy(input$manualMetricSelectionTF))  
  if (input$manualMetricSelectionTF== T){
   x$switchTrigger=1 
  }
  
})


observeEvent(x$keep,{ # if column names are updated, update x$x
  
  x$x=x$ensemble[, x$keep]
  
  cat(file=stderr(), 'x$keep', x$keep, "\n")  

  
}, ignoreInit = F)

```


```{r, define cases of interest}

y=reactiveValues(nCOI=0)

observeEvent(input$COIButton, {
  
  validate(need(!is.na(thresholds$thresholds[1]), "Please select thresholds via the violin plots."))

  AndOrTF=ifelse(input$AndOr == "And", T, F)
  
  y$COI=defineCOI(objectives_names = thresholds$objectives, objectives_data = obj$filter, thresholds=thresholds$thresholds, AndOrTF = AndOrTF)
  
  y$nCOI=sum(y$COI) # create output variable telling the number of COI. Use in valueBox function
  
  y$nonCOI=length(y$COI)-sum(y$COI)

  y$Trigger=1
  
  update$thresholds=0
  update$ensemble=0
  update$policy=0
  update$AndOr=0
  
}, ignoreNULL = T, ignoreInit = T)

observeEvent(input$COImanual, {
  
  AndOrTF=ifelse(input$AndOr == "And", T, F)
  
  # add objective and threshold

  c=1
  for (i in 1:length(input$SDObj)){
    
    name=input$SDObj[i]

    if (max(obj_all[,name])==input[[paste0("Thresh",i)]]){
      # do not save, user has not used this objective
    } else{
      
      thresholds$objectives[c]=name
      thresholds$thresholds[c]=input[[paste0("Thresh",i)]][1]
      c=c+1 # increase index only when you have added to the vectors
    }
    
    
  }

  
  y$COI=defineCOI(objectives_names = thresholds$objectives, objectives_data = obj$filter, thresholds=thresholds$thresholds, AndOrTF = AndOrTF)

  y$nCOI=sum(y$COI) # create output variable telling the number of COI. Use in valueBox function

  y$nonCOI=length(y$COI)-sum(y$COI)

  y$Trigger=1

  thresholds$ManualThresholdsTrigger=thresholds$ManualThresholdsTrigger+1
  
  update$thresholds=0
  update$ensemble=0
  update$policy=0
  update$AndOr=0
  
  
})


```

```{r, calculate boxes}

coverage=NA; density=NA # to create a dataframe for selected point in peeling trajectory
box=reactiveValues(Data=NA,PlotTrigger=0, selected=data.frame(coverage, density), oldSelected=data.frame(coverage, density) )

observeEvent(input$SDButton, {
  
  req(x$x)
  if(length(x$keep)<2){
    showNotification(id="MoreMetrics", "Please select at least two observable conditions.", duration = NULL, type = "warning")
  }
  req(length(x$keep)>1)
  req(y$COI)

  showNotification(id="CalculatePT", "Calculating. This may take a couple minutes...", duration = NULL)
  
  if(input$PRIMType==FALSE){ # MO PRIM
   
      box$Data=MO.PRIM(x=x$x, y=y$COI, qp_val=input$QPval, peel_crit = as.numeric(input$peel_crit), peel_alpha=input$PeelAlpha)


  } else {
    
    temp=prim(x=x$x, y=y$COI, peel_crit = as.numeric(input$peel_crit), remove_dims = T, peel.alpha=input$PeelAlpha)
    
     dimensions=vector()
        for (i in 1:length(temp$dimlist)){
          dimensions[i]=sum(temp$dimlist[[i]]$either)
        }

    box.metrics=data.frame(coverage=temp$relcoverage, density=temp$y.mean, dimensions, id=1:length(temp$x))
    
    add_to_box=list(box.metrics=box.metrics, box.info=temp)
    
    box$Data=add_to_box
    
  }

    removeNotification(id="CalculatePT")
    
    box$PlotTrigger=box$PlotTrigger+1
    
    showNotification("Plotting")
  
    update$PRIMalg=0 #remove asterisks from button and PT title
    update$thresholds2=0
    update$ensemble2=0
    update$policy2=0
    update$AndOr2=0
    
})

```

### 

```{r, peeling trajectory}

observeEvent( list(update$thresholds2, update$ensemble2, update$PRIMalg, update$policy2, update$AndOr2) ,{

  update$PTtitle=ifelse(sum(update$thresholds2, update$ensemble2, update$PRIMalg, update$policy2, update$AndOr2) > 0,
  "*Peeling trajectory*",
  "Peeling trajectory"
  )

  
})




fluidRow(column(width = 10, offset = 0,
              renderText({update$PTtitle})  
              ),
         column(width=1, offset=1,
    circleButton(inputId = "openPTModal", icon = icon("info-circle"), size = "xs", style="margin-botom: 0px; margin-top: 0px")
                )
         
         )
hr(style="margin-botom: 0px; margin-top: 5px; margin-left: -10px", width="110%")

output$dynamic=renderPlotly({
  
  box$PlotTrigger
  input$SDButton # re-render whenever SDButton is hit
  
  req(isTruthy(box$Data))
  
  data=box$Data$box.metrics
  data$dimensions=factor(data$dimensions)
  data$ID=1:nrow(data)

  static=ggplot(data=data, aes(x=coverage, y=density, color=dimensions, customdata=ID))+ # by assigning ID to customdata, you preserve sequential and unique ID of the boxes
  geom_point(size=3, alpha=0.65, position = "jitter")+
  coord_cartesian(ylim=c(0,1), xlim=c(0, 1))+
  scale_color_brewer(type = "diverging", palette = "RdYlBu",direction = -1)#+
  #theme(plot.margin=margin(t=0, r=0, b=10, l=0, unit='pt'))

  dynamic=ggplotly(static, source = "PT")

  dynamic=layout(dynamic, margin=list(b=100, r=100))
  
  dynamic
  

  
})

plotlyOutput("dynamic")

# monitor user clicks on peeling trajectory

observeEvent(eventExpr = event_data("plotly_click", source = "PT"),{

  temp=event_data("plotly_click", source = "PT")
  
  box$ID=temp$customdata
  
  box$selected$coverage=box$Data$box.metrics$coverage[temp$customdata] # update coverage and density of the selected point
  box$selected$density=box$Data$box.metrics$density[temp$customdata]
  
  
  # cat(file=stderr(), 'coverage, density = ', c(box$selected$coverage,box$selected$density), "\n") # prints dimension to R console
  
  xnew=box$selected$coverage
  xold=box$oldSelected$coverage
  ynew=box$selected$density
  yold=box$selected$density
    
  ndim=max(box$Data$box.metrics$dimensions) # this will be the plotly index of the trace that always needs deleted
  
  plotlyProxy("dynamic", session) %>%
    plotlyProxyInvoke("deleteTraces", list(as.integer(ndim))) %>%
    plotlyProxyInvoke("addTraces", list(x=c(xnew,xnew),y=c(ynew, ynew),
                        type = 'scatter',
                        mode = 'markers', marker = list(
        size=20, color="transparent",
        line = list(
        color = 'black',
        width = 3)
          )
        , name="selected")
                          )
  
  box$oldSelected$coverage=xnew
  box$oldSelected$density=ynew
  
  
})



```



Column
------------------------

### Scenario boxes

```{r}

observeEvent(list(input$SDButton, input$DurFreq, input$policyID), { # if SD is rerun, reset the box ID so scenario boxes pairs plot is removed
  box$ID=NULL
  # y$Trigger=0

}, ignoreInit = T)

save=reactiveValues() # create reactive value to save range_plot. It can then be saved to the database for comparing polices and scenarios

renderPlot({

validate(need(x$x, "Select observable conditions on the Define vulnerability page."))
validate(need(y$COI, "Define vulnerability thresholds using the violin plots on the Define vulnerability page."))
validate(need(box$Data, 'Perform scenario discovery then select a point from the peeling trajectory.'))
  
req(isTruthy(box$Data$box.info))
req(isTruthy(y$COI))
req(isTruthy(x$keep))
req(isTruthy(x$x))
validate(need(box$ID, 'Select a point from the peeling trajectory.'))

input$SDButton # replot if Perform Scenario Discovery button is hit
 
yCOI=isolate(y$COI) 
Vulnerable=ifelse(yCOI==1, "Yes", "No")

dim_names=isolate(x$keep) # will show all dimensions input to PRIM

sig_dim_names=names(box$Data$box.info$dimlist[[box$ID]]$either)[which(box$Data$box.info$dimlist[[box$ID]]$either==TRUE)] # will only show significant dimensions
save$ndim=length(sig_dim_names)

x=isolate(x$x)
metrics=data.frame(x[,dim_names])
colnames(metrics)=dim_names

box_lims=data.frame(box$Data$box.info$box[[box$ID]])

colnames(box_lims)=sig_dim_names

# add columns for the unconstrained dimensions

add=matrix(NA, ncol=length(dim_names)-length(sig_dim_names), nrow = 2)
add=data.frame(add)
colnames(add)=dim_names[!(dim_names %in% sig_dim_names)]

box_lims=data.frame(box_lims, add)

# cat(file=stderr(), 'box_lims:', colnames(box_lims), "\n") # prints dimension to R console

points=data.frame(metrics, Vulnerable)

add_plot=range_plot(box_lims = box_lims, x=x, units=units, annotation_size=input$RangePlotFont) # box looking plots of metric range

save$range_plot=add_plot

  test_var=if(input$PlotSignificant==FALSE){sig_dim_names} else {dim_names} # check if all or only significant metrics being plotted

if (length(test_var)>1){ # use ggpairs if 2 plus variables to plot

  DurFreq=isolate(input$DurFreq)

  # if(DurFreq==TRUE){labelSize=12; tickSize=10} else { labelSize=16; tickSize=11}# change text size depending on number of metrics
  
  labelSize=input$SDscatterLabel
  tickSize=input$SDscatterTick
  
  diagInput=if(input$SDDiagonalTF==T){list(continuous = modified_density)} else {list(continuous = "blankDiag")}
  
  if(input$PlotSignificant==FALSE){columns=sig_dim_names}else{columns=colnames(points)[-length(points)]}
  
  pairs=ggpairs(data=points, columns = columns,
        aes(color=Vulnerable, alpha=0.3),
        lower = list(continuous=wrap(SD_plot, dim_names=dim_names, box_lims=box_lims)),
        upper="blank", legend=NULL, switch="both", title="Scenario box constraints",
        diag = diagInput)+
        theme(text=element_text(size=labelSize))
  
  pairs=pairs+theme(axis.text.x = element_text(angle=90, size=tickSize), axis.text.y = element_text(size=tickSize))
  
  temp=pairs[2,1] # extract plot to steal legend from

  temp=temp+theme(legend.key = element_rect(fill = "transparent", colour = "transparent"),
                rect = element_rect(fill = "white")) # make legend background transparent

  legend=get_legend(temp) #steal legend
  legend=as_ggplot(legend) # convert to ggplot


  
  if(DurFreq==TRUE){width=.45; height=.72; x=.775; y=.68} else {width=.42; height=.62;x=.79; y=.72}# change viewport size depending on number of metrics
  
  xlegend=input$SDlegendx
  ylegend=input$SDlegendy
  
  if( input$SDDiagonalTF==F){
      pairs=gpairs_lower(pairs) # remove extra labels when diagonal not wanted
  }
  
  
  vp=viewport(width = width, height=height, x=x, y=y) # viewport for add plot
  vp2=viewport(width = 0.1, height=0.2, x=xlegend, y=ylegend) # viewport for legend
  print(pairs)
  print(add_plot, vp=vp)
  print(legend, vp=vp2)
  
} else { # single scatter plot with arbitrary y axis index
  
  # determine if upper, lower, or both constraints are used
  
  my_cols=c("No"="blue", "Yes"="red")
  points$index=1:nrow(points)
  
  p1=ggplot(data=points, aes(y=.data[[sig_dim_names]], x=index, color=Vulnerable))+
    geom_point(size=4.5, alpha=0.3)+
    geom_hline(yintercept=box_lims[2,1])+
    geom_hline(yintercept=box_lims[1,1])+
    scale_y_continuous(limits=range(points[[sig_dim_names]]))+
    theme(legend.position = c(.93,.93))+
    scale_colour_manual(values=my_cols)
  
  plot_grid(p1, add_plot, nrow=1, rel_widths = c(1/2, 1/2))

}

  
})




```


3.Compare policies and scenarios {data-orientation=columns}
==============================================================

```{r, save scenarios to database}

database=reactiveValues(names=list())

observeEvent(input$SaveScenario,{
  
  if(input$ScenarioName %in% names(database$names)){ # tell user when name has already been used
    showNotification(ui = "This name is already in use! Please create a new one.",duration = 10, type = "error")
    
  }
  
  req(!(input$ScenarioName %in% names(database$names))) # do not save if name already used
  
    ID=input$policyID
    nCOI=paste0(y$nCOI, " / ", length(y$COI))
    obj_thresh=thresholds$table
    plot=save$range_plot
    box_stats=data.frame(metric=c("coverage", "density", "dimensions"), value=c(box$selected$coverage, box$selected$density, save$ndim))
    box_lims=data.frame(box$Data$box.info$box[[box$ID]])
    sig_dim_names=names(box$Data$box.info$dimlist[[box$ID]]$either)[which(box$Data$box.info$dimlist[[box$ID]]$either==TRUE)]
    colnames(box_lims)=sig_dim_names

    database$names[[input$ScenarioName]]=list(name=input$ScenarioName, ID=ID, nCOI=nCOI, obj_thresh=obj_thresh, range_plot=plot, box_stats=box_stats, algorithm=algorithm$name, window=input$Window, includeDurFreq=input$DurFreq, QThreshType=input$QThreshType, SOWensemble=input$SOWensemble, box_lims=box_lims)

    showNotification("Scenario has been saved. You can now view it on the -Compare policies and scenarios- page.")
    
})

```


```{r, choose analysis to display}

# h4(strong("Choose up to four scenarios to display"), align="left")

fixedPanel(top="7%", left = "3%", style="z-index: 1000", width="98%",

fluidRow(column(width=2,
  renderUI({
  selectInput(inputId = "saved1",label = NULL , choices = c("Select analysis", names(database$names)), selected = NULL, width = "350px")
})    
      ),

column(width=1,
       
       splitLayout(cellWidths = c("35%", "35%"),
                  downloadButton(outputId = "Download1", icon = icon("download"), width="20%", style="margin-botom: 0px; margin-top: 0px", label=NULL),
                   circleButton(inputId = "Delete1", icon = icon("trash"), size = "sm", style="margin-botom: 0px; margin-top: 0px")
                   )
       
       
       
       
       ),

         column(width=2,
                
    renderUI({
  selectInput(inputId = "saved2",label = NULL , choices = c("Select analysis", names(database$names)), selected = NULL, width = "350px")
})             
                ),

    column(width=1,
       
       splitLayout(cellWidths = c("35%", "35%"),
                  downloadButton(outputId = "Download2", icon = icon("download"), width="20%", style="margin-botom: 0px; margin-top: 0px", label=NULL),
                   circleButton(inputId = "Delete2", icon = icon("trash"), size = "sm", style="margin-botom: 0px; margin-top: 0px")
                   )
       
       
       ),
         column(width=2,
                
    renderUI({
  selectInput(inputId = "saved3",label = NULL , choices = c("Select analysis", names(database$names)), selected = NULL, width = "350px")
})             
                
                
                ),

column(width=1,
       
              splitLayout(cellWidths = c("35%", "35%"),
                  downloadButton(outputId = "Download3", icon = icon("download"), width="20%", style="margin-botom: 0px; margin-top: 0px", label=NULL),
                   circleButton(inputId = "Delete3", icon = icon("trash"), size = "sm", style="margin-botom: 0px; margin-top: 0px")
                   )
       
       
       ),

         column(width=2,
      
    renderUI({
  selectInput(inputId = "saved4",label = NULL , choices = c("Select analysis", names(database$names)), selected = NULL, width = "350px")
}) 
                            
                          ),
column(width=1,
       
              splitLayout(cellWidths = c("35%", "35%"),
                  downloadButton(outputId = "Download4", icon = icon("download"), width="20%", style="margin-botom: 0px; margin-top: 0px", label=NULL),
                   circleButton(inputId = "Delete4", icon = icon("trash"), size = "sm", style="margin-botom: 0px; margin-top: 0px")
                   )
       
       
       )

         )

)





```

```{r, download and delete analyses}

################# download ###################


  
output$Download1=downloadHandler(filename =function(){paste0(input$saved1, ".rds")},content = function(file){

  saveRDS(database$names[[input$saved1]], file)
  })

output$Download2=downloadHandler(filename =function(){paste0(input$saved2, ".rds")},content = function(file){

  saveRDS(database$names[[input$saved2]], file)
  })

output$Download3=downloadHandler(filename =function(){paste0(input$saved3, ".rds")},content = function(file){

  saveRDS(database$names[[input$saved3]], file)
  })

output$Download4=downloadHandler(filename =function(){paste0(input$saved4, ".rds")},content = function(file){

  saveRDS(database$names[[input$saved4]], file)
  })



################# delete #####################

observeEvent(input$Delete1, {
  
  database$names[[input$saved1]]=NULL
   #cat(file=stderr(), 'your name:',names(database$names), "\n") # prints dimension to R console
   
})
observeEvent(input$Delete2, {
  
  database$names[[input$saved2]]=NULL
   #cat(file=stderr(), 'your name:',names(database$names), "\n") # prints dimension to R console
   
})
observeEvent(input$Delete3, {
  
  database$names[[input$saved3]]=NULL
   #cat(file=stderr(), 'your name:',names(database$names), "\n") # prints dimension to R console
   
})
observeEvent(input$Delete4, {
  
  database$names[[input$saved4]]=NULL
   #cat(file=stderr(), 'your name:',names(database$names), "\n") # prints dimension to R console
   
})


```



Column {style="height:125pc; position:relative;"}
-----------------------------

###

```{r, compare 1}

div(style="margin-bottom: 3pc")

output$DV1=renderPlotly({
  
  req(input$saved1)
  req(input$saved1 != "Select analysis")
  #req(((input$HideMead %% 2)== 0) )
  
  data=database$names[[input$saved1]]
  
  # cat(file=stderr(), 'ID', data$ID, "\n")
  
  DV_plot(to_plot=data$ID, metric_label="order", preferred_direction="min", y_axis2=F)
}) 

div(style="margin-bottom: 10px")

metrics1=c("policy ID","SOW ensemble")
metrics2=c("algorithm", "coverage", "density", "dimensions" )

div(align="left", 
      
      h4(strong("1. Define vulnerability thresholds"))
      
      )
hr()

fluidRow(column(width = 10, offset = 1,

      div(align="center",
          
         h5(strong("Policy ID & SOW ensemble")) 
          ),
      
                 
        renderTable({
  
  req(input$saved1)
  req(input$saved1 != "Select analysis")
  
  data=database$names[[input$saved1]]
  values1=c(data$ID, data$SOWensemble)
 
  data.frame(metrics1, values1)
  
  
  }, striped = T, bordered = T, spacing = "m", rownames = F, colnames = F),

  
  div(align="center", h5(strong("Lake Mead operation diagram")))
  
 

))




fluidRow(column(width = 10, offset = 0,

      plotlyOutput("DV1")
      
                    
  )
)
 
  
fluidRow(column(width = 10, offset = 1,
         
    div(align="center", 
      
  h5(strong("Vulnerability thresholds"))
      
  ),
  
  renderTable({
        req(input$saved1)
        req(input$saved1 != "Select analysis")
        
        temp=database$names[[input$saved1]]$obj_thresh
        
        temp
        
    }, striped = T, bordered = T, spacing = "m", rownames = F, colnames = T),
  

    div(align="center",
        renderText(paste0("Number of vulnerable cases: ", database$names[[input$saved1]]$nCOI))
        )

         ))

div(align="left", 
      
  h4(strong("2. Perform Scenario Discovery"))
      
)

hr()

fluidRow(column(width = 10, offset = 1,
                
div(align="center", 
      
  h5(strong("Algorithm & scenario metrics"))
      
),
  
  renderTable({
    
  req(input$saved1)
  req(input$saved1 != "Select analysis")
  
  data=database$names[[input$saved1]]
  
  values2=c(data$algorithm, round(data$box_stats[1:2,2],2), round(data$box_stats[3,2],2))
  
  data.frame(metrics=metrics2, values=values2)

  }, striped = T, bordered = T, spacing = "m", rownames = F, colnames = F),
  
div(align="center", 
      
  h5(strong("Uncertainty metric constraints"))
  
)
))

renderPlot({

  req(input$saved1)
  req(input$saved1 != "Select analysis")

  data=database$names[[input$saved1]]

  data$range_plot

  }, width = 450, height = 900)                    

```


Column {style="height:125pc;"}
-----------------------

###

```{r, compare 2}

div(style="margin-bottom: 3pc")

output$DV2=renderPlotly({
  
  req(input$saved2)
  req(input$saved2 != "Select analysis")
  #req(((input$HideMead %% 2)== 0) )
  
  data=database$names[[input$saved2]]
  
  # cat(file=stderr(), 'ID', data$ID, "\n")
  
  DV_plot(to_plot=data$ID, metric_label="order", preferred_direction="min", y_axis2=F)
}) 


div(style="margin-bottom: 10px")


div(align="left", 
      
      h4(strong("1. Define vulnerability thresholds"))
      
      )
hr()

fluidRow(column(width = 10, offset = 1,

      div(align="center",
          
         h5(strong("Policy ID & SOW ensemble")) 
          ),
      
                 
        renderTable({
  
  req(input$saved2)
  req(input$saved2 != "Select analysis")
  
  data=database$names[[input$saved2]]
  values1=c(data$ID, data$SOWensemble)
 
  data.frame(metrics1, values1)
  
  
  }, striped = T, bordered = T, spacing = "m", rownames = F, colnames = F),

  
  div(align="center", h5(strong("Lake Mead operation diagram")))
  
  

))




fluidRow(column(width = 10, offset = 0,
                
      plotlyOutput("DV2")
            
  )
)
 
  
fluidRow(column(width = 10, offset = 1,
         
    div(align="center", 
      
  h5(strong("Vulnerability thresholds"))
      
  ),
  
  renderTable({
        req(input$saved2)
        req(input$saved2 != "Select analysis")
        
        temp=database$names[[input$saved2]]$obj_thresh
        
        temp
        
    }, striped = T, bordered = T, spacing = "m", rownames = F, colnames = T),
  

    div(align="center",
        renderText(paste0("Number of vulnerable cases: ", database$names[[input$saved2]]$nCOI))
        )

         ))

div(align="left", 
      
  h4(strong("2. Perform Scenario Discovery"))
      
)

hr()

fluidRow(column(width = 10, offset = 1,
                
div(align="center", 
      
  h5(strong("Algorithm & scenario metrics"))
      
),
  
  renderTable({
    
  req(input$saved2)
  req(input$saved2 != "Select analysis")
  
  data=database$names[[input$saved2]]
  
  values2=c(data$algorithm, round(data$box_stats[1:2,2],2), round(data$box_stats[3,2],2))
  
  data.frame(metrics=metrics2, values=values2)

  }, striped = T, bordered = T, spacing = "m", rownames = F, colnames = F),
  
div(align="center", 
      
  h5(strong("Uncertainty metric constraints"))
  
)
))

renderPlot({

  req(input$saved2)
  req(input$saved2 != "Select analysis")

  data=database$names[[input$saved2]]

  data$range_plot

  }, width = 450, height = 900)   
```

Column {style="height:125pc;"}
-----------------------

### 

```{r, compare 3}

div(style="margin-bottom: 3pc")

output$DV3=renderPlotly({
  
  req(input$saved3)
  req(input$saved3 != "Select analysis")
  #req(((input$HideMead %% 2)== 0) )
  
  data=database$names[[input$saved3]]
  
  # cat(file=stderr(), 'ID', data$ID, "\n")
  
  DV_plot(to_plot=data$ID, metric_label="order", preferred_direction="min", y_axis2=F)
}) 


div(style="margin-bottom: 10px")

metrics1=c("policy ID","SOW ensemble")
metrics2=c("algorithm", "coverage", "density", "dimensions" )

div(align="left", 
      
      h4(strong("1. Define vulnerability thresholds"))
      
      )
hr()

fluidRow(column(width = 10, offset = 1,

      div(align="center",
          
         h5(strong("Policy ID & SOW ensemble")) 
          ),
      
                 
        renderTable({
  
  req(input$saved3)
  req(input$saved3 != "Select analysis")
  
  data=database$names[[input$saved3]]
  values1=c(data$ID, data$SOWensemble)
 
  data.frame(metrics1, values1)
  
  
  }, striped = T, bordered = T, spacing = "m", rownames = F, colnames = F),

  
  div(align="center", h5(strong("Lake Mead operation diagram")))
  

))




fluidRow(column(width = 10, offset = 0,


      plotlyOutput("DV3")
           
  )
)
 
  
fluidRow(column(width = 10, offset = 1,
         
    div(align="center", 
      
  h5(strong("Vulnerability thresholds"))
      
  ),
  
  renderTable({
        req(input$saved3)
        req(input$saved3 != "Select analysis")
        
        temp=database$names[[input$saved3]]$obj_thresh
        
        temp
        
    }, striped = T, bordered = T, spacing = "m", rownames = F, colnames = T),
  

    div(align="center",
        renderText(paste0("Number of vulnerable cases: ", database$names[[input$saved3]]$nCOI))
        )

         ))

div(align="left", 
      
  h4(strong("2. Perform Scenario Discovery"))
      
)

hr()

fluidRow(column(width = 10, offset = 1,
                
div(align="center", 
      
  h5(strong("Algorithm & scenario metrics"))
      
),
  
  renderTable({
    
  req(input$saved3)
  req(input$saved3 != "Select analysis")
  
  data=database$names[[input$saved3]]
  
  values2=c(data$algorithm, round(data$box_stats[1:2,2],2), round(data$box_stats[3,2],2))
  
  data.frame(metrics=metrics2, values=values2)

  }, striped = T, bordered = T, spacing = "m", rownames = F, colnames = F),
  
div(align="center", 
      
  h5(strong("Uncertainty metric constraints"))
  
)
))

renderPlot({

  req(input$saved3)
  req(input$saved3 != "Select analysis")

  data=database$names[[input$saved3]]

  data$range_plot

  }, width = 450, height = 900)   
```

Column {style="height:125pc;"}
-----------------------

###

```{r, compare 4}

div(style="margin-bottom: 3pc")

output$DV4=renderPlotly({
  
  req(input$saved4)
  req(input$saved4 != "Select analysis")
  #req(((input$HideMead %% 2)== 0) )
  
  data=database$names[[input$saved4]]
  
  # cat(file=stderr(), 'ID', data$ID, "\n")
  
  DV_plot(to_plot=data$ID, metric_label="order", preferred_direction="min", y_axis2=F)
}) 


div(style="margin-bottom: 10px")

metrics1=c("policy ID","SOW ensemble")
metrics2=c("algorithm", "coverage", "density", "dimensions" )

div(align="left", 
      
      h4(strong("1. Define vulnerability thresholds"))
      
      )
hr()

fluidRow(column(width = 10, offset = 1,

      div(align="center",
          
         h5(strong("Policy ID & SOW ensemble")) 
          ),
      
                 
        renderTable({
  
  req(input$saved4)
  req(input$saved4 != "Select analysis")
  
  data=database$names[[input$saved4]]
  values1=c(data$ID, data$SOWensemble)
 
  data.frame(metrics1, values1)
  
  
  }, striped = T, bordered = T, spacing = "m", rownames = F, colnames = F),

  
  div(align="center", h5(strong("Lake Mead operation diagram")))
  

))




  fluidRow(column(width = 10, offset = 0,
                

      plotlyOutput("DV4")
        
  )
)
 
  
fluidRow(column(width = 10, offset = 1,
         
    div(align="center", 
      
  h5(strong("Vulnerability thresholds"))
      
  ),
  
  renderTable({
        req(input$saved4)
        req(input$saved4 != "Select analysis")
        
        temp=database$names[[input$saved4]]$obj_thresh
        
        temp
        
    }, striped = T, bordered = T, spacing = "m", rownames = F, colnames = T),
  

    div(align="center",
        renderText(paste0("Number of vulnerable cases: ", database$names[[input$saved4]]$nCOI))
        )

         ))

div(align="left", 
      
  h4(strong("2. Perform Scenario Discovery"))
      
)

hr()

fluidRow(column(width = 10, offset = 1,
                
div(align="center", 
      
  h5(strong("Algorithm & scenario metrics"))
      
),
  
  renderTable({
    
  req(input$saved4)
  req(input$saved4 != "Select analysis")
  
  data=database$names[[input$saved4]]
  
  values2=c(data$algorithm, round(data$box_stats[1:2,2],2), round(data$box_stats[3,2],2))
  
  data.frame(metrics=metrics2, values=values2)

  }, striped = T, bordered = T, spacing = "m", rownames = F, colnames = F),
  
div(align="center", 
      
  h5(strong("Uncertainty metric constraints"))
  
)
))

renderPlot({

  req(input$saved4)
  req(input$saved4 != "Select analysis")

  data=database$names[[input$saved4]]

  data$range_plot

  }, width = 450, height = 900)   
```

Top-down scenario imposition {data-orientation=columns}
================================

Inputs {.sidebar data-width=500}
--------------------------------

```{r top-down scenario inputs}



fluidRow(column(width=6, #style='margin-bottom:15px;margin-right: 0px; border:1px solid; padding: 10px;',
      
    h5("Define your own scenario"),
    hr(),
    selectInput(inputId = "TDmetrics", label = "Choose observable conditions", choices = colnames(SOW_all[-c(4,5)]), multiple = T, width = "95%"),
    
    renderUI({
    req(length(input$TDmetrics) >=1)
      
    #my_step=if(grep(pattern = "Q.",x = input$TDmetrics[1])){0.5} else {NULL}

    sliderInput("TDmetric1", label=paste0(input$TDmetrics[1], " range"),# step = my_step,
                min=round(min(SOW_all[[input$TDmetrics[1]]]),2),
                max=round(max(SOW_all[[input$TDmetrics[1]]]), 2), value=round(c(min(SOW_all[[input$TDmetrics[1]]]),max(SOW_all[[input$TDmetrics[1]]])),2), ticks = F
                )
    
    
    }),
    renderUI({
    req(length(input$TDmetrics) >=2)
      
    #my_step=if(grep(pattern = "Q.",x = input$TDmetrics[2])){0.5}else {NULL}
      
    sliderInput("TDmetric2", label=paste0(input$TDmetrics[2], " range"),# step = my_step,
                min=round(min(SOW_all[[input$TDmetrics[2]]]),2),
                max=round(max(SOW_all[[input$TDmetrics[2]]]), 2), value=round(c(min(SOW_all[[input$TDmetrics[2]]]),max(SOW_all[[input$TDmetrics[2]]])),2), ticks = F
                )
    
    
    }),
    renderUI({
    req(length(input$TDmetrics) >=3)
    sliderInput("TDmetric3", label=paste0(input$TDmetrics[3], " range"), min=round(min(SOW_all[[input$TDmetrics[3]]]),2),
                max=round(max(SOW_all[[input$TDmetrics[3]]]), 2), value=round(c(min(SOW_all[[input$TDmetrics[3]]]),max(SOW_all[[input$TDmetrics[3]]])),2), ticks = F
                )
    
    
    }),
    renderUI({
    req(length(input$TDmetrics) >=4)
    sliderInput("TDmetric4", label=paste0(input$TDmetrics[4], " range"), min=round(min(SOW_all[[input$TDmetrics[4]]]),2),
                max=round(max(SOW_all[[input$TDmetrics[4]]]), 2), value=round(c(min(SOW_all[[input$TDmetrics[4]]]),max(SOW_all[[input$TDmetrics[4]]])),2), ticks = F
                )
    
    
    }),
    renderUI({
    req(length(input$TDmetrics) >=5)
    sliderInput("TDmetric5", label=paste0(input$TDmetrics[5], " range"), min=round(min(SOW_all[[input$TDmetrics[5]]]),2),
                max=round(max(SOW_all[[input$TDmetrics[5]]]), 2), value=round(c(min(SOW_all[[input$TDmetrics[5]]]),max(SOW_all[[input$TDmetrics[5]]])),2), ticks = F
                )
    
    
    }),
    renderUI({
    req(length(input$TDmetrics) >=6)
    sliderInput("TDmetric6", label=paste0(input$TDmetrics[6], " range"), min=round(min(SOW_all[[input$TDmetrics[6]]]),2),
                max=round(max(SOW_all[[input$TDmetrics[6]]]), 2), value=round(c(min(SOW_all[[input$TDmetrics[6]]]),max(SOW_all[[input$TDmetrics[6]]])),2), ticks = F
                )
    
    
    }),
    renderUI({
    req(length(input$TDmetrics) >=7)
    sliderInput("TDmetric7", label=paste0(input$TDmetrics[7], " range"), min=round(min(SOW_all[[input$TDmetrics[7]]]),2),
                max=round(max(SOW_all[[input$TDmetrics[7]]]), 2), value=round(c(min(SOW_all[[input$TDmetrics[7]]]),max(SOW_all[[input$TDmetrics[7]]])),2), ticks = F
                )
    
    
    })
      
      
      
                
                ), ################# end column for slider inputs ###############
    
    column(width=6,
                         
      h5("Choose from saved scenarios"),
      hr(),
      fileInput(inputId = "uploadScenario", label = "Upload scenario .rds", accept = ".rds", width = "95%", multiple = T),
      renderUI({
  selectInput(inputId = "TDsaved",label = "Select scenario(s)" , choices = names(database$names), selected = NULL, width = "95%", multiple = T )
}),


checkboxGroupInput(inputId = "whichBox",label = "Which box(es) to plot", choices = list("self-defined"=1, "saved"=2),inline = F, width = "95%", selected = c(1,2))

)
                         
         ) # end fluidRow for Defining scenarios

hr(style="margin-top: 10px; margin-bottom: 10px")

fluidRow(column(width=6,
                
       selectizeInput(inputId = "TDpolicyID",label = "Select 1-2 policy(s) to compare", choices = c(1:nrow(wide_data)),
               options = list(maxItems = 2), selected = NULL, multiple = T, width="90%"),

selectInput(inputId = "TDSOWensemble", label = "Choose SOW ensemble", choices = c("cLHS 300", "cLHS 500"), selected = "cLHS 300", width="90%"),

  prettyToggle(inputId = "DefaultVulnerability", label_on = "Use vulnerabilities defined on page 1",label_off = "Define vulnerability here", value = T),

renderUI({
  req(TDcalcs$scen_names)
  radioButtons(inputId = "ScenarioTable", label = "Scenario to display in table", choices = TDcalcs$scen_names)

}),

    dropdownButton(circle = F, label = "Plot settings", width = "120%",
                   
                   prettyToggle(inputId = "TDDiagonalTF",label_on = "Remove kernel density plots", label_off = "Include kernel density plots", value = T),
                   
                  sliderInput(inputId = "TDlegendx",label = "legend x position", min = -0.5, max = 1,value = 0.1, step = 0.01, width="90%", ticks = F),
                  sliderInput(inputId = "TDlegendy",label = "legend y position", min = 0.00, max = 1,value = 0.94, step = 0.01, width="90%", ticks = F),      
                  sliderInput(inputId = "TDscatterLabel", label = "Axis label font size", min = 10, max = 30, value = 16, step = 0.5,width = "90%", ticks = F),
                  sliderInput(inputId = "TDscatterTick", label = "Tick font size", min = 8, max = 26, value = 12, step = 0.5,width = "90%", ticks = F)
         )
                
                ), column(width=6,
                          
     # renderUI({
     #   req(length(input$TDObj >=1))
     #   h5("Vulnerability thresholds")
     # }),
     #  renderUI({
     #   req(length(input$TDObj >=1))
     #   hr()
     # }),
    
    
    renderUI({
      req(input$DefaultVulnerability==F)
      selectInput("TDObj",label="Select objectives", multiple = T, choices=colnames(obj_all)[-c(1,2)])
      
    }),
    
    renderUI({
      req(input$DefaultVulnerability==F)
      radioButtons(inputId = "AndOrTD", label = "Condition for multiple objectives", choices = c("Or", "And"), inline = T)
    
    }), 
     
     
    renderUI({
    req(length(input$TDObj) >=1 & input$DefaultVulnerability==F)
    sliderInput("TDThresh1", label=paste0(input$TDObj[1], " threshold"), min=min(obj_all[[input$TDObj[1]]]),
                max=max(obj_all[[input$TDObj[1]]]), value=max(obj_all[[input$TDObj[1]]]), ticks = F)
    }),
    
    renderUI({
    req(length(input$TDObj) >=2 & input$DefaultVulnerability==F)
    sliderInput("TDThresh2", label=paste0(input$TDObj[2], " threshold"), min=min(obj_all[[input$TDObj[2]]]),
                max=max(obj_all[[input$TDObj[2]]]), value=max(obj_all[[input$TDObj[2]]]), ticks = F)
    }),
    
    renderUI({
    req(length(input$TDObj) >=3 & input$DefaultVulnerability==F)
    sliderInput("TDThresh3", label=paste0(input$TDObj[3], " threshold"), min=min(obj_all[[input$TDObj[3]]]),
                max=max(obj_all[[input$TDObj[3]]]), value=max(obj_all[[input$TDObj[3]]]), ticks = F)
    }),
    
    renderUI({
    req(length(input$TDObj) >=4 & input$DefaultVulnerability==F)
    sliderInput("TDThresh4", label=paste0(input$TDObj[4], " threshold"), min=min(obj_all[[input$TDObj[4]]]),
                max=max(obj_all[[input$TDObj[4]]]), value=max(obj_all[[input$TDObj[4]]]), ticks = F)
    }),
    
    renderUI({
    req(length(input$TDObj) >=5 & input$DefaultVulnerability==F)
    sliderInput("TDThresh5", label=paste0(input$TDObj[5], " threshold"), min=min(obj_all[[input$TDObj[5]]]),
                max=max(obj_all[[input$TDObj[5]]]), value=max(obj_all[[input$TDObj[5]]]), ticks = F)
    }),

    renderUI({
    req(length(input$TDObj) >=6 & input$DefaultVulnerability==F)
    sliderInput("TDThresh6", label=paste0(input$TDObj[6], " threshold"), min=min(obj_all[[input$TDObj[6]]]),
                max=max(obj_all[[input$TDObj[6]]]), value=max(obj_all[[input$TDObj[6]]]), ticks = F)
    }),

    renderUI({
    req(length(input$TDObj) >=7 & input$DefaultVulnerability==F)
    sliderInput("TDThresh7", label=paste0(input$TDObj[7], " threshold"), min=min(obj_all[[input$TDObj[7]]]),
                max=max(obj_all[[input$TDObj[7]]]), value=max(obj_all[[input$TDObj[7]]]), ticks = F)
    }),

    renderUI({
    req(length(input$TDObj) >=8 & input$DefaultVulnerability==F)
    sliderInput("TDThresh8", label=paste0(input$TDObj[8], " threshold"), min=min(obj_all[[input$TDObj[8]]]),
                max=max(obj_all[[input$TDObj[8]]]), value=max(obj_all[[input$TDObj[8]]]), ticks = F)
    }),

    renderUI({
    req(length(input$TDObj) >=9 & input$DefaultVulnerability==F)
    sliderInput("TDThresh9", label=paste0(input$TDObj[9], " threshold"), min=min(obj_all[[input$TDObj[9]]]),
                max=max(obj_all[[input$TDObj[9]]]), value=max(obj_all[[input$TDObj[9]]]), ticks = F)
    }),
    
    renderUI({
      req(length(input$TDObj) >=1 & input$DefaultVulnerability==F)
      actionButton(inputId = "COITD", label = "Apply thresholds & plot", width = "80%")
      
    })
    
    
                )
)



```


```{r, process user inputted scenarios}


observe({
  
  req(isTruthy(input$TDmetrics))
  
  UDbox_lims=data.frame(matrix(nrow = 2, ncol=length(input$TDmetrics)))


  for(i in 1:length(input$TDmetrics)){
    req(isTruthy(input[[paste0("TDmetric",i)]]))
    UDbox_lims[1:2,i]=input[[paste0("TDmetric",i)]]
    
  }

  
  colnames(UDbox_lims)=input$TDmetrics
  
  TDcalcs$UDbox_lims=UDbox_lims
  
  # cat(file=stderr(), 'your name:', colnames(UDbox_lims), "\n") # prints dimension to R console
  # cat(file=stderr(), 'your name:', UDbox_lims[,1], "\n") # prints dimension to R console

})

observeEvent(input$uploadScenario, {


  for (i in 1: nrow(input$uploadScenario)){
    
    dataFile=input$uploadScenario[1,]
     if(is.null(dataFile)){
       next
     } else {
       upload=readRDS(dataFile$datapath)
      #cat(file=stderr(), 'your name:', upload[["name"]], "\n") # prints dimension to R console

     }
  
    if(is.null(database$names)){
      database$names=list()
      database$names[[upload$name]]=upload
    } else if(upload$name %in% names(database$names)){
      showNotification(paste("The scenario named -",upload[["name"]], "- already exists. Please remove the scenario with the same name before trying to upload."),type = "warning")
      next
    } else {
      database$names[[upload$name]]=upload
    }

    #cat(file=stderr(), 'your name:', names(database$names), "\n") # prints dimension to R console
    
  }

  
  
  
})


```



SOW and scenario
----------------------------------

```{r, calculate COI top-down page}

TDcalcs=reactiveValues()

observeEvent(list(input$DefaultVulnerability,thresholds$objectives,thresholds$thresholds), {
  
  req(input$DefaultVulnerability)
  
  if(input$DefaultVulnerability==T){
    TDcalcs$objectives=thresholds$objectives
    TDcalcs$thresholds=thresholds$thresholds
  }
  
}, ignoreInit = F)


observeEvent(input$COITD, { # if Apply button is hit, recalculate TDcalcs
  
      TDcalcs$objectives=input$TDObj
  

  # add objective and threshold

        c=1
        for (i in 1:length(input$TDObj)){
          
          name=input$TDObj[i]
      
          if (max(obj_all[,name])==input[[paste0("TDThresh",i)]]){
            # do not save, user has not used this objective
          } else{
            
            TDcalcs$objectives[c]=name
            TDcalcs$thresholds[c]=input[[paste0("TDThresh",i)]][1]
            c=c+1 # increase index only when you have added to the vectors
          }
          
          
        }
 
}, ignoreInit = T)

observeEvent(list(TDcalcs$objectives, TDcalcs$thresholds, input$TDpolicyID, input$TDSOWensemble, input$AndOrTD, input$DefaultVulnerability, thresholds$thresholds, thresholds$objectives),{ # calculate COI for selected policies, objectives, and thresholds
  
  req(TDcalcs$objectives)
  req(TDcalcs$thresholds)
  
  validate(need(expr = input$TDpolicyID,message = "Select policy(s)"))
  
  if(input$DefaultVulnerability==T){
    AndOrTF=ifelse(input$AndOr == "And", T, F)
  } else {
    req(input$AndOrTD)
    AndOrTF=ifelse(input$AndOrTD == "And", T, F)
  }
      
  objData=dplyr::filter(obj_all, ID == input$TDpolicyID[1])
  
  if(input$TDSOWensemble=="cLHS 300"){
    
    objData=objData[SOW_500_300_100[[2]]$model,]
  
  }
  
  req(length(TDcalcs$objectives)>0)
  req(length(TDcalcs$thresholds)>0)

  TDcalcs$IDaCOI=defineCOI(objectives_names = TDcalcs$objectives, objectives_data = objData, thresholds=TDcalcs$thresholds, AndOrTF = AndOrTF)


    if(length(input$TDpolicyID)>1){# if two polices were selected, calculate COI for policy B
      
      objData=dplyr::filter(obj_all, ID == input$TDpolicyID[2])
  
      if(input$TDSOWensemble=="cLHS 300"){
        
        objData=objData[SOW_500_300_100[[2]]$model,]
      
      }
      
      temp=defineCOI(objectives_names = TDcalcs$objectives, objectives_data = objData, thresholds=TDcalcs$thresholds, AndOrTF = AndOrTF)
  
      TDcalcs$IDbCOI=ifelse(temp==1, 1.1, 0) # give a unique number to track that policy B is vulnerable, as opposed to policy A above
      
      temp=rowSums(data.frame(TDcalcs$IDaCOI, TDcalcs$IDbCOI))
      # cat(file=stderr(), 'your name:', TDcalcs$IDaCOI[1:20], "\n") # prints dimension to R console
      # cat(file=stderr(), 'your name:', TDcalcs$IDbCOI[1:20], "\n") # prints dimension to R console
      # 
      #cat(file=stderr(), 'your name:', temp, "\n") # prints dimension to R console
      
      temp[temp==2.1]="Both vulnerable"
      temp[temp==1]="First policy vulnerable"
      temp[temp==1.1]="Second policy vulnerable"
      temp[temp==0]="Neither vulnerable"
      
      TDcalcs$IDabCOI=temp
      
      # cat(file=stderr(), 'your name:', which(TDcalcs$IDabCOI[1:20]), "\n") # prints dimension to R console
      
    }
  
  
})


observeEvent(list(input$TDsaved, TDcalcs$UDbox_lims, input$whichBox), {

TDcalcs$box_list=list()
TDcalcs$scen_names=c()

  if (1 %in% input$whichBox & isTruthy(input$TDmetric1)){ # 1 corresponds to self-defined box

    TDcalcs$box_list[[1]]=TDcalcs$UDbox_lims
    TDcalcs$scen_names[1]="user-defined"
    
  }

  if(2 %in% input$whichBox){ # 2 corresponds to saved boxes

    req(input$TDsaved)
    si=length(TDcalcs$box_list)
    for(i in 1:length(input$TDsaved)){
      
      TDcalcs$box_list[[input$TDsaved[i]]]=database$names[[input$TDsaved[i]]]$box_lims
      TDcalcs$scen_names[si+i]=input$TDsaved[i]
    }


  }


}, ignoreInit = T)

########### calculate summary statistics table #############


observeEvent(list(input$ScenarioTable, input$TDpolicyID, TDcalcs$box_list, input$TDSOWensemble
                  ),{
  #findme
  
  req(input$ScenarioTable)
  req(input$TDpolicyID)
  req(TDcalcs$box_list)

  if(input$TDSOWensemble =="cLHS 300"){
    SOW=SOW_500_300_100[[2]]$SOW
  } else {
    SOW=SOW_500_300_100[[1]]$SOW
  }
  
  #cat(file=stderr(), 'your name:', "a", "\n") # prints dimension to R console

  
  if(input$ScenarioTable=="user-defined"){
    boxID=1
  } else {
    boxID=input$ScenarioTable
  }


  
  box=TDcalcs$box_list[[boxID]]
    cat(file=stderr(), 'metrics:', colnames(box), "\n") # prints dimension to R console

  req(box)  
  ndims=ncol(box)
  
  aCalcs=matrix(nrow=nrow(SOW), ncol=ndims+1)
  bCalcs=matrix(nrow=nrow(SOW), ncol=ndims+1)

  
  for(i in 1:ndims){ # loop through metrics in box, label within each box dimension range
    
    name=colnames(box)[i]
    
    aCalcs[,i]=(SOW[[name]] >= box[[name]][1]) & (SOW[[name]] <= box[[name]][2])
    if(length(input$TDpolicyID)>1){
      bCalcs[,i]=(SOW[[name]] >= box[[name]][1]) & (SOW[[name]] <= box[[name]][2])
    }
  }
  
  if(ndims>1){
    tempa=rowSums(aCalcs[,1:ndims]) # sum of rows tells you how many dimension of SOW are in the scenario

  } else {
    tempa=aCalcs[,1:ndims]
  }

  aCalcs[,ndims+1]=ifelse(tempa == ndims, 1, 0) # assign 1 if within box

  
  tempa=aCalcs[,ndims+1]+TDcalcs$IDaCOI # if sum is 2, then vulnerable and in scenario
    #cat(file=stderr(), 'tempa', tempa, "\n") # prints dimension to R console

  TDcalcs$IDaDensity=sum(tempa==2)/sum(aCalcs[,ndims+1]==1) # number of vulnerable points in box/total number of points in box
  TDcalcs$IDaCoverage=sum(tempa==2)/sum(TDcalcs$IDaCOI==1)
  
  IDaVector=c(paste0(sum(TDcalcs$IDaCOI),"/",nrow(SOW)), round(TDcalcs$IDaCoverage,2), round(TDcalcs$IDaDensity,2))

  TDcalcs$table=data.frame(IDaVector)
  colnames(TDcalcs$table)=paste("ID:", input$TDpolicyID[1])
  row.names(TDcalcs$table)= c("total vulnerable cases", "coverage", "density")
  
  if(length(input$TDpolicyID)>1){
    
      if(ndims>1){
    tempb=rowSums(bCalcs[,1:ndims]) # sum of rows tells you how many dimension of SOW are in the scenario

        } else {
          tempb=bCalcs[,1:ndims]
      }
    
      bCalcs[,ndims+1]=ifelse(tempb == ndims, 1, 0) # assign 1 if within box
      tempb=bCalcs[,ndims+1] + TDcalcs$IDbCOI
      TDcalcs$IDbDensity=sum(tempb==2.1)/sum(bCalcs[,ndims+1]==1) # number of vulnerable points in box/total number of points in box
      TDcalcs$IDbCoverage=sum(tempb==2.1)/sum(TDcalcs$IDbCOI==1.1)
    
        IDbVector=c(paste0(sum(TDcalcs$IDbCOI==1.1),"/",nrow(SOW)), round(TDcalcs$IDbCoverage,2), round(TDcalcs$IDbDensity,2))

      TDcalcs$table=cbind(IDaVector, IDbVector)
      colnames(TDcalcs$table)=c(paste("ID:", input$TDpolicyID[1]),paste("ID:", input$TDpolicyID[2]) )
  row.names(TDcalcs$table)= c("total vulnerable cases", "coverage", "density")
      
  }

  
  #cat(file=stderr(), 'stats', #c(TDcalcs$IDaDensity,TDcalcs$IDaCoverage,TDcalcs$IDbDensity,TDcalcs$IDbCoverage), "\n") # prints dimension to R console


})




```


### Scenario boxes and SOW scatter matrix
```{r, top-down scatter matrix}

################## prep SOW dataframe ###############
observeEvent(input$TDSOWensemble, {
      if (input$TDSOWensemble == "cLHS 300"){TDcalcs$ensemble=SOW_500_300_100[[2]]$SOW} else {TDcalcs$ensemble=SOW_500_300_100[[1]]$SOW}
})

renderPlot({

  validate(need(isTruthy(input$TDmetrics[2])| isTruthy(input$TDsaved), "Select at least two observable conditions or select a saved scenario to plot."))

  if(!isTruthy(input$TDmetrics[1]) & isTruthy(input$TDsaved)){
      box=TDcalcs$box_list[[input$TDsaved]]
      ndims=ncol(box)

      validate(need(ndims>1, "The selected scenario is 1-dimensional. Please choose another observable condition to plot."))
    

  }
  
  validate(need(input$TDpolicyID, "Select policy(s)."))
  validate(need(TDcalcs$IDaCOI, "Define vulnerability on page 1 or to the left."))
  validate(need(isTruthy(input$whichBox), "Select which box(es) to plot."))

  
  
  labelSize=input$TDscatterLabel
  tickSize=input$TDscatterTick
  
  x=input$TDlegendx
  y=input$TDlegendy


    box_lims=TDcalcs$box_list
    
    ###### get metric names to be plotted ###########
    
    all_names=c()
    if (isTruthy(input$TDmetrics) & (1 %in% input$whichBox)){
      all_names=input$TDmetrics
    }
  
    #cat(file=stderr(), 'all metrics:', all_names, "\n") # prints dimension to R console

    if(isTruthy(input$TDsaved) & (2 %in% input$whichBox)){
      for(i in 1:length(input$TDsaved)){
        all_names=c(all_names, colnames(TDcalcs$box_list[[input$TDsaved[i]]]))
        
      }
      
      if(length(all_names)<2){ #add a metric so you can plot 1D saved scenarios
        all_names[2]=input$TDmetrics[1]
      }
      
    }
    
    all_names=unique(all_names)
    #cat(file=stderr(), 'all metrics:', all_names, "\n") # prints dimension to R console
   #cat(file=stderr(), 'your name:',TDcalcs$scen_names, "\n")
  
  if(length(input$TDpolicyID)==1){ # plot for only one policy
  
    diagInput=if(input$TDDiagonalTF==T){list(continuous = modified_density)} else {list(continuous = "blankDiag")}


    Vulnerable=ifelse(TDcalcs$IDaCOI==1, "Yes", "No")
    TDcalcs$ensemble$Vulnerable=Vulnerable

    pairs_TD=ggpairs(data=TDcalcs$ensemble, columns = all_names,
        aes(color=Vulnerable, alpha=0.3),
        lower =  list(continuous=wrap(SD_plot2, box_lims=box_lims, npolicy=1, name_vec=TDcalcs$scen_names)),
        upper=list(continuous = "blank"), legend=NULL, switch="both", title="Vulnerable SOW",
        diag = diagInput)+
        theme(text=element_text(size=labelSize))


  } else { # two policies
    
    diagInput=if(input$TDDiagonalTF==T){list(continuous = modified_density2)} else {list(continuous = "blankDiag")}

    
    Vulnerable=TDcalcs$IDabCOI
    TDcalcs$ensemble$Vulnerable=Vulnerable
    
    pairs_TD=ggpairs(data=TDcalcs$ensemble, columns = all_names,
        aes(color=Vulnerable, shape=Vulnerable, fill=Vulnerable, alpha=0.3),
        lower = list(continuous=wrap(SD_plot2, box_lims=box_lims, npolicy=2, name_vec=TDcalcs$scen_names)),
        upper=list(continuous = "blank"), legend=NULL, switch="both", title="Vulnerable SOW",
        diag = diagInput)+
        theme(text=element_text(size=labelSize))

  }

   
  #### create dummy rectangle plot to steal legend from #####
   
   scen_legend=scenario_legend(scen_names=TDcalcs$scen_names, colors=c("black", "red", "purple", "green", "brown", "orange", "yellow", "pink"), size=1)
    
   
   
  pairs_TD=pairs_TD+theme(axis.text.x = element_text(angle=90, size=tickSize), axis.text.y =element_text(size=tickSize))
  
    temp_TD=pairs_TD[2,1] # extract plot to steal legend from
  
    temp_TD=temp_TD+theme(legend.key = element_rect(fill = "transparent", colour = "transparent"),
                  rect = element_rect(fill = "white")) # make legend background transparent
  
    legend_TD=get_legend(temp_TD) #steal legend
    legend_TD=as_ggplot(legend_TD) # convert to ggplot
  
    if( input$TDDiagonalTF==F){
        pairs_TD=gpairs_lower(pairs_TD) # remove extra labels when diagonal not wanted
    }

    vp_TD=viewport(width = 1, height=4, x=x, y=y, just = "left") # viewport for COI
    vp_scenLegend=viewport(width=1, height=2, x=x,y=y-.1, just="left") # viewport for scenario names
    print(pairs_TD)
    print(legend_TD, vp=vp_TD)
    print(scen_legend, vp=vp_scenLegend)


})

```

```{r TD page absolute panel}

absolutePanel(class = "panel panel-default", fixed = T,
                draggable = TRUE, top = 100, left = "auto", right = 20, bottom = "auto",
                width = '20%', height = 'auto',
                style = "overflow-y:scroll; max-height: 1000px; opacity: 0.9; style = z-index: 400",

              h4(strong("Scenario statistics")),
              
                 HTML('<button data-toggle="collapse"  data-target="#boxTD1" class="btn-block btn-primary"></button>'),
   tags$div(id = 'boxTD1', class="collapse in",

      renderTable(TDcalcs$table, rownames = T, colnames = T)
      
      )

   )


```



